---
title: "Dube 2012w"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../scripts/auxiliary_functions.R")
source("../scripts/summary_plots.R")

load("dubep_orig.eqn-Dube_2012-P.csv.RData")
results1 <- results

load("dubep_qrest.eqn-Dube_2012-P.csv.RData")
results2 <- results

load("dubep_rrest.eqn-Dube_2012-P.csv.RData")
results3 <- results
```

###Experiment summary


### Some information on the models

**Model Original:** q_2 = q_5, & r_2 = r_5 (all but highest confidence response mapping of uncertainty and detection states equated)  
**Q restricted:** q_2 = q_5 (all but highest confidence response mapping of uncertainty states equated)  
**R restricted:** r_2 = r_5 (all but highest confidence response mapping of detection states equated)  

### Some information on convergence

#### For Model Original
One approach failed:
partial, TreeBUGS, beta

Frequentist approach with no pooling (asymptotic.no.MPTinR) had 0.682 as proportion of participants with non-identified parameters.
Frequentist approach with complete pooling (asymptotic.complete.MPTinR) had no convergence problems.  

Bayesian approach with no pooling (simple.no.TreeBUGS) and with complete pooling (simple.complete.TreeBUGS) both converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs and trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05.  

#### For Q restricted
One approach failed:
partial, TreeBUGS, beta

Frequentist approach with no pooling (asymptotic.no.MPTinR) had 0.909 as proportion of participants with non-identified parameters.
Frequentist approach with complete pooling (asymptotic.complete.MPTinR) had some convergence problems:  
rank.fischer = 4, n.parameters = 10, convergence = 0.  

Bayesian approach with no pooling (simple.no.TreeBUGS) and with complete pooling (simple.complete.TreeBUGS) both converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs and trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05. 

#### For R restricted
One approach failed:
partial, TreeBUGS, beta

Frequentist approach with no pooling (asymptotic.no.MPTinR) had 0.591 as proportion of participants with non-identified parameters.
Frequentist approach with complete pooling (asymptotic.complete.MPTinR) had no convergence problems.  

Bayesian approach with no pooling (simple.no.TreeBUGS) and with complete pooling (simple.complete.TreeBUGS) both converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs and trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05. 

### Parameter estimation

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=7} 
pars <- bind_rows(unnest(results1, est_group))

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

ggplot(pars,aes(y = est, x = parameter, 
                col=interaction(method, pooling,package),
                shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Original Model')+
  scale_shape_manual(values=shapes) +
  theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```

**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=7}
pars <- bind_rows(unnest(results2, est_group))

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))


ggplot(pars,aes(y = est, x = parameter, 
                col=interaction(method, pooling,package),
                shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Q Restricted')+
  scale_shape_manual(values=shapes) +
  theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=7}
pars <- bind_rows(unnest(results3, est_group))

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))


ggplot(pars,aes(y = est, x = parameter, 
                col=interaction(method, pooling,package),
                shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for R Restricted')+
  scale_shape_manual(values=shapes) +
  theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**Core parameters**
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
pars <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))

pars$model <- ifelse(pars$model=='dubep_orig.eqn',
                     'Original Model',
                     ifelse(pars$model=='dubep_qrest.eqn',
                            'Q Restricted',
                            'R Restricted'))

core <- filter(pars, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est, x = model,
                 col=interaction(method, pooling,package),
                 shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() +
  facet_wrap(~parameter) +
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()


ggplot(core, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_wrap(~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
```
**Q parameters**

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=8}
params_q <- filter(pars, parameter %in% c("q_1", "q_2", "q_5", "q_6"))
ggplot(params_q, aes(y = est, x = model,
                     col=interaction(method, pooling,package),
                     shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  facet_wrap(~parameter, ncol = 4) +
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()

ggplot(params_q, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_wrap(~parameter, ncol = 4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
```
**R parameters**

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=8}
params_r <- filter(pars, parameter %in% c("r_1", "r_2", "r_5", "r_6"))
ggplot(params_r, aes(y = est, x = model,
                     col=interaction(method, pooling,package),
                     shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  facet_wrap(~parameter, ncol=4) +
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of R Parameters Across Models')+
  theme_bw() +
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()

ggplot(params_r, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
 facet_wrap(~parameter, ncol = 4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_shape_manual(values=shapes) +
   scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
   labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of R Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
```

### Goodness of fit

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results1, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                      'No',
                      ifelse(gof$pooling=="complete",
                             'Comp',
                             'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                      'MR',
                      'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                     'PB',
                     ifelse(gof$method=="asymptotic",
                            'asy',
                            ifelse(gof$method=="simple",
                                   '',
                                   ifelse(gof$method=="trait",
                                          'trait',
                                          ifelse(gof$method=="trait_uncorrelated",
                                                 'trait_u',
                                                 'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                    'Mean',
                    ifelse(gof$focus=="cov",
                           'Covariance',
                           gof$focus))


ggplot(gof, aes(y = p, 
                x = interaction(method, pooling, package))) + 
  geom_point(size=2) + ylim(0, 1) + 
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  labs(x='Analysis approach',y='p value', title='Goodness of fit: Original model')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```
**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results2, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                      'No',
                      ifelse(gof$pooling=="complete",
                             'Comp',
                             'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                      'MR',
                      'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                     'PB',
                     ifelse(gof$method=="asymptotic",
                            'asy',
                            ifelse(gof$method=="simple",
                                   '',
                                   ifelse(gof$method=="trait",
                                          'trait',
                                          ifelse(gof$method=="trait_uncorrelated",
                                                 'trait_u',
                                                'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                    'Mean',
                    ifelse(gof$focus=="cov",
                           'Covariance',
                           gof$focus))


ggplot(gof, aes(y = p, 
                x = interaction(method, pooling, package))) + 
  geom_point(size=2) + ylim(0, 1) + 
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  labs(x='Analysis approach',y='p value', title='Goodness of fit: Q restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results3, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                      'No',
                      ifelse(gof$pooling=="complete",
                             'Comp',
                             'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                      'MR',
                      'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                     'PB',
                     ifelse(gof$method=="asymptotic",
                            'asy',
                            ifelse(gof$method=="simple",
                                   '',
                                   ifelse(gof$method=="trait",
                                          'trait',
                                          ifelse(gof$method=="trait_uncorrelated",
                                                 'trait_u',
                                                'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                    'Mean',
                    ifelse(gof$focus=="cov",
                           'Covariance',
                           gof$focus))


ggplot(gof, aes(y = p, 
                x = interaction(method, pooling, package))) + 
  geom_point(size=2) + ylim(0, 1) + 
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  labs(x='Analysis approach',y='p value', title='Goodness of fit: R restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```