---
title: "A Multiverse Pipeline for MPT models "
subtitle: "Applications to Recognition Memory"
author: "Henrik Singmann (Twitter: <a href='https://twitter.com/HenrikSingmann'>@HenrikSingmann</a>)<br/>Georgia Eleni Kapetaniou<br/>University of Zurich"
date: "April 2018"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "my-theme.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# see: https://github.com/yihui/xaringan
# install.packages("xaringan")
# see: 
# https://github.com/yihui/xaringan/wiki
# https://github.com/gnab/remark/wiki/Markdown
options(width=110)
options(digits = 4)
library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../../scripts/auxiliary_functions.R")
source("../../scripts/summary_plots.R")
load("../../broeder_exp1/model_orig.eqn-exp1.txt.RData")
results1 <- results

load("../../broeder_exp1/model_orig_qrest.eqn-exp1.txt.RData")
results2 <- results

load("../../broeder_exp1/model_orig_rrest.eqn-exp1.txt.RData")
results3 <- results
```


class: inline-grey
# Information on experiment procedure and conditions

- description
- manipulations etc

---

# Models

- Model restrictions
    - **Model Original:** q_2 = q_7, q_3 = q_6 & r_3 = r_6 (all but highest confidence response mapping of uncertainty states equated and lowest two confidence response mapping of detection states equated)
    - **Q restricted:** q_2 = q_7, q_3 = q_6 (all but highest confidence response mapping of uncertainty states equated) 
    - `model.matrix()` and factor codings.
    - **R restricted:** r_3 = r_6 (lowest two confidence response mapping of detection states equated)

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
gof <- bind_rows(unnest(results1, gof),
                 unnest(results2, gof),
                 unnest(results3, gof)
)

gof$pooling <- factor(gof$pooling, levels = c("no", "complete",  "partial"), 
                      labels = c("No", "Comp", "PP"))

gof$package <- factor(gof$package, levels = c("MPTinR", "TreeBUGS"), 
                      labels = c("MR", "TB"))
gof$method <- factor(gof$method, levels = c("PB/MLE", "asymptotic", "simple",
                                            "trait", "trait_uncorrelated"), 
                     labels = c("PB", "asy", "ss", "trait", "trait_u"))

gof$inter <- with(gof, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(gof$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                       "Comp.Bayes", "Trait.PP", "Trait_u.PP")

gof$focus <- factor(gof$focus, levels = c('cov', 'mean'),
                    labels = c('Covariance', 'Mean'))

gof$model <- factor(gof$model, levels = c('model_orig.eqn', 'model_orig_qrest.eqn', 'model_orig_rrest.eqn'),
                    labels = c('Q & R Restr.', 'Q Restricted', 'R Restricted'))

ggplot(gof, aes(y = p, 
                x = inter, col=model)) + 
  geom_point(size=5) +  
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) +
  labs(x='Analysis approach',y= expression(italic(p)), 
       color='Model', title='Goodness of fit')+
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
pars <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

pars$condition <- factor(pars$condition, levels = c('strong_naming', 'weak_naming'),
                         labels = c('Strong wording', 'Weak wording'))

pars$pooling <- factor(pars$pooling, levels = c('no','complete','partial'),
                       labels = c('No', 'Comp', 'PP'))

pars$package <- factor(pars$package, levels = c("MPTinR", "TreeBUGS"), 
                      labels = c("MR", "TB"))

pars$method <- factor(pars$method, levels = c("PB/MLE", "asymptotic", "simple",
                                            "trait", "trait_uncorrelated"), 
                     labels = c("PB", "asy", "ss", "trait", "trait_u"))

pars$inter <- with(pars, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(pars$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                       "Comp.Bayes", "Trait.PP", "Trait_u.PP")

pars$model <- factor(pars$model, levels = c('model_orig.eqn', 'model_orig_qrest.eqn', 'model_orig_rrest.eqn'),
                    labels = c('Q & R Restr.', 'Q Restricted', 'R Restricted'))


shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .8)

core <- filter(pars, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est, x = inter,
                 shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) + 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
core <- filter(pars, parameter %in% c("Do", "Dn", "g") & condition %in% c('Strong wording'))
ggplot(core, aes(y = est, x = inter,
                 shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) + 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
core <- filter(pars, parameter %in% c("Do", "Dn", "g") & condition %in% c('Weak wording'))
ggplot(core, aes(y = est, x = inter,
                 shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) + 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
core <- filter(pars, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est, x = model,
                 col=inter,
                 shape=inter)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) +  
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
core <- filter(pars, parameter %in% c("Do", "Dn", "g") & condition %in% c('Strong wording'))
ggplot(core, aes(y = est, x = model,
                 col=inter,
                 shape=inter)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) +  
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
core <- filter(pars, parameter %in% c("Do", "Dn", "g") & condition %in% c('Weak wording'))
ggplot(core, aes(y = est, x = model,
                 col=inter,
                 shape=inter)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) +  
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
res_between <- bind_rows(
  unnest(results1, test_between),
  unnest(results2, test_between),
  unnest(results3, test_between)
)

res_between$pooling <- factor(res_between$pooling, levels = c('no','complete','partial'),
                       labels = c('No', 'Comp', 'PP'))

res_between$package <- factor(res_between$package, levels = c("MPTinR", "TreeBUGS"), 
                       labels = c("MR", "TB"))

res_between$method <- factor(res_between$method, levels = c("PB/MLE", "asymptotic", "simple",
                                              "trait", "trait_uncorrelated"), 
                      labels = c("PB", "asy", "ss", "trait", "trait_u"))

res_between$inter <- with(res_between, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(res_between$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                        "Comp.Bayes", "Trait.PP", "Trait_u.PP")

res_between$model <- factor(res_between$model, levels = c('model_orig.eqn', 'model_orig_qrest.eqn', 'model_orig_rrest.eqn'),
                     labels = c('Q & R Restr.', 'Q Restricted', 'R Restricted'))

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'


shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .8)

core <- filter(res_between, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est_diff, x = inter,
                  col=model,
                  shape=model)) +
  facet_wrap(~parameter, ncol=3)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.6)+
  geom_point(position = dd, size=3.5) + 
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1), 
                     labels = c("-1", "0", "1")) +  
  labs(x='Model',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Differences Between Conditions Across Models: Core Parameters')+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.35))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

params_q <- filter(pars, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8"))
ggplot(params_q, aes(y = est, x = inter,
                     shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=1),limits=c(0,1), 
                     labels = c("0", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  theme(text=element_text(size = 24))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

params_q <- filter(pars, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8") & condition %in% c('Strong wording'))
ggplot(params_q, aes(y = est, x = inter,
                     shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=1),limits=c(0,1), 
                     labels = c("0", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  theme(text=element_text(size = 24))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

params_q <- filter(pars, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8") & condition %in% c('Weak wording'))
ggplot(params_q, aes(y = est, x = inter,
                     shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=1),limits=c(0,1), 
                     labels = c("0", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  theme(text=element_text(size = 24))+
  coord_flip()


```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
params_q <- filter(res_between, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8"))
ggplot(params_q, aes(y = est_diff, x = inter,
                     col=model,
                     shape=model)) +
  facet_wrap(~parameter, ncol=6)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.6)+
  geom_point(position = dd, size=3.5) +  
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+ 
  labs(x='Model',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Differences Between Conditions Across Models: Q Parameters')+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.3))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

params_r <- filter(pars, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8"))
ggplot(params_r, aes(y = est, x = inter,
                     shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=1),limits=c(0,1), 
                     labels = c("0", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of R Parameters Across Models')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

params_r <- filter(pars, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8") & condition %in% c('Strong wording'))
ggplot(params_r, aes(y = est, x = inter,
                     shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=1),limits=c(0,1), 
                     labels = c("0", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of R Parameters Across Models')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

params_r <- filter(pars, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8") & condition %in% c('Weak wording'))
ggplot(params_r, aes(y = est, x = inter,
                     shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=1),limits=c(0,1), 
                     labels = c("0", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of R Parameters Across Models')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
params_r <- filter(res_between, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8"))
ggplot(params_r, aes(y = est_diff, x = inter,
                     col=model,
                     shape=model)) +
  facet_wrap(~parameter, ncol=6)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.6)+
  geom_point(position = dd, size=3.5) + 
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+ 
  labs(x='Model',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Differences Between Conditions Across Models: R Parameters')+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.3))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
load("../../dube2012p/dubep_orig.eqn-Dube_2012-P.csv.RData")
results1_2 <- results

load("../../dube2012p/dubep_qrest.eqn-Dube_2012-P.csv.RData")
results2_2 <- results

load("../../dube2012p/dubep_rrest.eqn-Dube_2012-P.csv.RData")
results3_2 <- results


load("../../dube2012w/dubew_orig.eqn-Dube_2012-W.csv.RData")
results1_3 <- results

load("../../dube2012w/dubeW_qrest.eqn-Dube_2012-W.csv.RData")
results2_3 <- results

load("../../dube2012w/dubeW_rrest.eqn-Dube_2012-W.csv.RData")
results3_3 <- results


load("../../heathcote2006e1/heathcote_orig.eqn-Heathcote_2006_e1.csv.RData")
results1_4 <- results

load("../../heathcote2006e1/heathcote_qrest.eqn-Heathcote_2006_e1.csv.RData")
results2_4 <- results

load("../../heathcote2006e1/heathcote_rrest.eqn-Heathcote_2006_e1.csv.RData")
results3_4 <- results


load("../../heathcote2006e2/heathcote2_orig.eqn-Heathcote_2006_e2.csv.RData")
results1_5 <- results

load("../../heathcote2006e2/heathcote2_qrest.eqn-Heathcote_2006_e2.csv.RData")
results2_5 <- results

load("../../heathcote2006e2/heathcote2_rrest.eqn-Heathcote_2006_e2.csv.RData")
results3_5 <- results


load("../../jaeger2012/jaeger_orig.eqn-Jaeger_2012.csv.RData")
results1_6 <- results

load("../../jaeger2012/jaeger_qrest.eqn-Jaeger_2012.csv.RData")
results2_6 <- results

load("../../jaeger2012/jaeger_rrest.eqn-Jaeger_2012.csv.RData")
results3_6 <- results



load("../../koen2013/koen_orig.eqn-Koen_2013_immediate.csv.RData")
results1_7 <- results

load("../../koen2013/koen_qrest.eqn-Koen_2013_immediate.csv.RData")
results2_7 <- results

load("../../koen2013/koen_rrest.eqn-Koen_2013_immediate.csv.RData")
results3_7 <- results


gof_a <- bind_rows(
  unnest(results1_2, gof),
  unnest(results2_2, gof),
  unnest(results3_2, gof),
  unnest(results1_3, gof),
  unnest(results2_3, gof),
  unnest(results3_3, gof),
  unnest(results1_4, gof),
  unnest(results2_4, gof),
  unnest(results3_4, gof),
  unnest(results1_5, gof),
  unnest(results2_5, gof),
  unnest(results3_5, gof),
  unnest(results1_6, gof),
  unnest(results2_6, gof),
  unnest(results3_6, gof),
  unnest(results1_7, gof),
  unnest(results2_7, gof),
  unnest(results3_7, gof),
)

gof_a$pooling <- factor(gof_a$pooling, levels = c("no", "complete",  "partial"), 
                      labels = c("No", "Comp", "PP"))

gof_a$package <- factor(gof_a$package, levels = c("MPTinR", "TreeBUGS"), 
                      labels = c("MR", "TB"))
gof_a$method <- factor(gof_a$method, levels = c("PB/MLE", "asymptotic", "simple",
                                            "trait", "trait_uncorrelated","beta"), 
                     labels = c("PB", "asy", "ss", "trait", "trait_u","beta"))

gof_a$inter <- with(gof_a, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(gof_a$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                       "Comp.Bayes", "Trait.PP", "Trait_u.PP","Beta.PP")

gof_a$focus <- factor(gof_a$focus, levels = c('cov', 'mean'),
                    labels = c('Covariance', 'Mean'))

gof_a$model <- ifelse(gof_a$model=="dubep_orig.eqn"|gof_a$model=="jaeger_orig.eqn"|gof_a$model=="koen_orig.eqn"|gof_a$model=="koen_orig.eqn"|gof_a$model=="koen_orig.eqn"|gof_a$model=="heathcote_orig.eqn"|gof_a$model=="heathcote_orig.eqn"|gof_a$model=="dubew_orig.eqn"|gof_a$model=="heathcote2_orig.eqn"|gof_a$model=="koen_orig.eqn",
                       'Q & R Restr.',
                       ifelse(gof_a$model=="dubep_qrest.eqn"|gof_a$model=="jaeger_qrest.eqn"|gof_a$model=="koen_qrest.eqn"|gof_a$model=="heathcote_qrest.eqn"|gof_a$model=="dubew_qrest.eqn"|gof_a$model=="heathcote2_qrest.eqn"|gof_a$model=="koen_qrest.eqn",
                              'Q Restricted',
                              ifelse(gof_a$model=="dubep_rrest.eqn"|gof_a$model=="jaeger_rrest.eqn"|gof_a$model=="koen_rrest.eqn"|gof_a$model=="heathcote_rrest.eqn"|gof_a$model=="dubew_rrest.eqn"|gof_a$model=="heathcote2_rrest.eqn"|gof_a$model=="koen_rrest.eqn",
                                     'R Restricted',
                                     gof_a$model)))

gof_a$dataset <- factor(gof_a$dataset, levels = c("exp1.txt", "Dube_2012-P.csv", "Dube_2012-W.csv", "Heathcote_2006_e1.csv", "Heathcote_2006_e2.csv", "Jaeger_2012.csv", "Koen_2013_immediate.csv"), 
                         labels = c("Broeder et al. (2013)", "Dube & Rotello (2012, P)", "Dube & Rotello (2012, W)","Heathcote et al. (2006, 1)","Heathcote et al. (2006, 2)","Jaeger et al. (2012)","Koen et al. (2013)"))


gof_all <- filter(gof_a, focus %in% c("Mean"))
ggplot(gof_all, aes(y = p, 
                x = inter, col=dataset)) + 
  geom_point(size=5) +  
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~model,ncol = 3) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) +
  labs(x='Analysis approach',y= expression(italic(p)), 
       color='Dataset', title='Goodness of fit')+
  theme(text=element_text(size = 22))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))


```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

params <- bind_rows(
  unnest(results1_2, est_group),
  unnest(results2_2, est_group),
  unnest(results3_2, est_group),
  unnest(results1_3, est_group),
  unnest(results2_3, est_group),
  unnest(results3_3, est_group),
  unnest(results1_4, est_group),
  unnest(results2_4, est_group),
  unnest(results3_4, est_group),
  unnest(results1_5, est_group),
  unnest(results2_5, est_group),
  unnest(results3_5, est_group),
  unnest(results1_6, est_group),
  unnest(results2_6, est_group),
  unnest(results3_6, est_group),
  unnest(results1_7, est_group),
  unnest(results2_7, est_group),
  unnest(results3_7, est_group),
)

params$pooling <- factor(params$pooling, levels = c("no", "complete",  "partial"), 
                      labels = c("No", "Comp", "PP"))

params$package <- factor(params$package, levels = c("MPTinR", "TreeBUGS"), 
                      labels = c("MR", "TB"))
params$method <- factor(params$method, levels = c("PB/MLE", "asymptotic", "simple",
                                                "trait", "trait_uncorrelated","beta"), 
                       labels = c("PB", "asy", "ss", "trait", "trait_u","beta"))

params$inter <- with(params, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(params$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                         "Comp.Bayes", "Trait.PP", "Trait_u.PP","Beta.PP")

params$model <- ifelse(params$model=="dubep_orig.eqn"|params$model=="jaeger_orig.eqn"|params$model=="koen_orig.eqn"|params$model=="koen_orig.eqn"|params$model=="koen_orig.eqn"|params$model=="heathcote_orig.eqn"|params$model=="heathcote_orig.eqn"|params$model=="dubew_orig.eqn"|params$model=="heathcote2_orig.eqn"|params$model=="koen_orig.eqn",
                             'Q & R Restr.',
                       ifelse(params$model=="dubep_qrest.eqn"|params$model=="jaeger_qrest.eqn"|params$model=="koen_qrest.eqn"|params$model=="heathcote_qrest.eqn"|params$model=="dubew_qrest.eqn"|params$model=="heathcote2_qrest.eqn"|params$model=="koen_qrest.eqn",
                              'Q Restricted',
                              ifelse(params$model=="dubep_rrest.eqn"|params$model=="jaeger_rrest.eqn"|params$model=="koen_rrest.eqn"|params$model=="heathcote_rrest.eqn"|params$model=="dubew_rrest.eqn"|params$model=="heathcote2_rrest.eqn"|params$model=="koen_rrest.eqn",
                                'R Restricted',
                                  params$model)))

params$dataset <- factor(params$dataset, levels = c("exp1.txt", "Dube_2012-P.csv", "Dube_2012-W.csv", "Heathcote_2006_e1.csv", "Heathcote_2006_e2.csv", "Jaeger_2012.csv", "Koen_2013_immediate.csv"), 
                         labels = c("Broeder et al. (2013)", "Dube & Rotello (2012, P)", "Dube & Rotello (2012, W)","Heathcote et al. (2006, 1)","Heathcote et al. (2006, 2)","Jaeger et al. (2012)","Koen et al. (2013)"))

Core_all <- filter(params, parameter %in% c("Dn","Do","g") & model %in% c('R Restricted'))
ggplot(Core_all, aes(y = est, x = inter,
                      color=dataset)) +
  facet_wrap( ~parameter, ncol=3) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Dataset', title='Core Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

Core_all <- filter(params, parameter %in% c("Dn","Do","g") & model %in% c('R Restricted'))
ggplot(Core_all, aes(y = est, x = dataset,
                  color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=3) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Dataset', y='Estimate', color='Analysis approach', shape='Analysis approach', title='Core Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

Q_all <- filter(params, parameter %in% c("q_1", "q_2", "q_5", "q_6") & model %in% c('R Restricted'))
ggplot(Q_all, aes(y = est, x = inter,
                     color=dataset)) +
  facet_wrap( ~parameter, ncol=4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Dataset', title='Q Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
Q_all <- filter(params, parameter %in% c("q_1", "q_2", "q_5", "q_6") & model %in% c('R Restricted'))
ggplot(Q_all, aes(y = est, x = dataset,
                  color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Dataset', y='Estimate', color='Analysis approach', shape='Analysis approach', title='Q Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 20))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
R_all <- filter(params, parameter %in% c("r_1", "r_2", "r_6") & model %in% c('R Restricted'))
ggplot(R_all, aes(y = est, x = inter,
                  color=dataset)) +
  facet_wrap( ~parameter, ncol=3) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Analysis approach', y='Estimate', color='Dataset', title='R Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
R_all <- filter(params, parameter %in% c("q_1", "q_2", "q_5", "q_6") & model %in% c('R Restricted'))
ggplot(R_all, aes(y = est, x = dataset,
                  color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Dataset', y='Estimate', color='Analysis approach', shape='Analysis approach', title='R Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 20))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small

### References 
- Bröder, A., Kellen, D., Schütz, J., & Rohrmeier, C. (2013). Validating a two-high-threshold measurement model for confidence rating data in recognition. *Memory*, 21(8), 916–944. https://doi.org/10.1080/09658211.2013.767348
- Dube, C., Starns, J. J., Rotello, C. M., & Ratcliff, R. (2012). Beyond ROC curvature: Strength effects and response time data support continuous-evidence models of recognition memory. *Journal of Memory and Language*, 67(3), 389–406. https://doi.org/10.1016/j.jml.2012.06.002
- Jaeger, A., Cox, J. C., & Dobbins, I. G. (2012). Recognition confidence under violated and confirmed memory expectations. *Journal of Experimental Psychology: General*, 141(2), 282–301. https://doi.org/10.1037/a0025687
- Koen, J. D., Aly, M., Wang, W.-C., & Yonelinas, A. P. (2013). Examining the causes of memory strength variability: Recollection, attention failure, or encoding variability? *Journal of Experimental Psychology: Learning, Memory, and Cognition*, 39(6), 1726–1741. https://doi.org/10.1037/a0033671
- Steegen, S., Tuerlinckx, F., Gelman, A., & Vanpaemel, W. (2016). Increasing Transparency Through a Multiverse Analysis. *Perspectives on Psychological Science*, 11(5), 702–712. https://doi.org/10.1177/1745691616658637
