---
title: "A Multiverse Pipeline for MPT models "
subtitle: "Applications to Recognition Memory"
author: "Henrik Singmann (Twitter: <a href='https://twitter.com/HenrikSingmann'>@HenrikSingmann</a>)<br/>Georgia Eleni Kapetaniou<br/>University of Zurich"
date: "April 2018"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "my-theme.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# see: https://github.com/yihui/xaringan
# install.packages("xaringan")
# see: 
# https://github.com/yihui/xaringan/wiki
# https://github.com/gnab/remark/wiki/Markdown
options(width=110)
options(digits = 4)
library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../../scripts/auxiliary_functions.R")
source("../../scripts/summary_plots.R")
load("../../broeder_exp1/model_orig.eqn-exp1.txt.RData")
results1 <- results

load("../../broeder_exp1/model_orig_qrest.eqn-exp1.txt.RData")
results2 <- results

load("../../broeder_exp1/model_orig_rrest.eqn-exp1.txt.RData")
results3 <- results
```


class: inline-grey
# Information on experiment procedure and conditions

- description
- manipulations etc

---

# Models

- Model restrictions
    - **Model Original:** q_2 = q_7, q_3 = q_6 & r_3 = r_6 (all but highest confidence response mapping of uncertainty states equated and lowest two confidence response mapping of detection states equated)
    - **Q restricted:** q_2 = q_7, q_3 = q_6 (all but highest confidence response mapping of uncertainty states equated) 
    - `model.matrix()` and factor codings.
    - **R restricted:** r_3 = r_6 (lowest two confidence response mapping of detection states equated)

---

class: small, center


```{r, echo = FALSE, warning=FALSE, fig.width=12, fig.height=8.5}
gof <- bind_rows(unnest(results1, gof),
                 unnest(results2, gof),
                 unnest(results3, gof)
)

gof$pooling <- ifelse(gof$pooling=="no",
                       'No',
                       ifelse(gof$pooling=="complete",
                              'Comp',
                              'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                       'MR',
                       'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                      'PB',
                      ifelse(gof$method=="asymptotic",
                             'asy',
                             ifelse(gof$method=="simple",
                                    '',
                                    ifelse(gof$method=="trait",
                                           'trait',
                                           ifelse(gof$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                      'Mean',
                      ifelse(gof$focus=="cov",
                             'Covariance',
                             gof$focus))

gof$model <- ifelse(gof$model=='model_orig.eqn',
                     'Original Model',
                     ifelse(gof$model=='model_orig_qrest.eqn',
                            'Q Restricted',
                            'R Restricted'))

ggplot(gof, aes(y = p, 
             x = interaction(method, pooling, package), col=model)) + 
  geom_point(size=3) + ylim(0, 1) + 
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  labs(x='Analysis approach',y='p value', color='Model', title='Goodness of fit')+
  theme(text=element_text(size = 16))+
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))

```

---

class: small, center


```{r, echo = FALSE, warning=FALSE, fig.width=12, fig.height=8.5}
pars <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

pars$condition <- ifelse(pars$condition=="strong_naming",
                         'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))

pars$model <- ifelse(pars$model=='model_orig.eqn',
                     'Original Model',
                     ifelse(pars$model=='model_orig_qrest.eqn',
                            'Q Restricted',
                            'R Restricted'))

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

core <- filter(pars, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2.5) + 
  ylim(0,1) + 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 16))+
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))+
  coord_flip()
```

---

class: small, center


```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=8.5}
core <- filter(pars, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est, x = model,
                 col=interaction(method, pooling,package),
                 shape=interaction(method, pooling,package))) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2.5) + 
  ylim(0,1) + 
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(text=element_text(size = 16))+
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))+
  coord_flip()
```

---

class: small, center


```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=8.5}
res_between <- bind_rows(
  unnest(results1, test_between),
  unnest(results2, test_between),
  unnest(results3, test_between)
)

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'

res_between$pooling <- ifelse(res_between$pooling=="no",
                       'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                       'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                      'PB',
                      ifelse(res_between$method=="asymptotic",
                             'as',
                             ifelse(res_between$method=="simple",
                                    '',
                                    ifelse(res_between$method=="trait",
                                           'trait',
                                           ifelse(res_between$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  res_between$method)))))
res_between$model <- ifelse(res_between$model=='model_orig.eqn',
                     'Original Model',
                     ifelse(res_between$model=='model_orig_qrest.eqn',
                            'Q Restricted',
                            'R Restricted'))
dd <- position_dodge(w = .75)
core2 <- filter(res_between, parameter %in% c("Do", "Dn", "g"))
ggplot(core2, aes(y = est_diff, x = model,
                  col=interaction(method, pooling,package),
                  shape=interaction(method, pooling,package))) +
  facet_wrap(~parameter, ncol=3)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2.5) + ylim(-1,1) + 
  labs(x='Model',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions Across Models: Core Parameters')+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  theme(text=element_text(size = 16))+
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))+
  coord_flip()
```

---

class: small, center


```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=12, fig.height=8.5}

params_q <- filter(pars, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8"))
ggplot(params_q, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1))+ 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))+
  theme(text=element_text(size = 16))+
  coord_flip()
```


---

class: small, center


```{r, echo = FALSE, warning=FALSE, fig.width=12, fig.height=8.5}
params_q <- filter(res_between, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8"))
ggplot(params_q, aes(y = est_diff, x = model,
                     col=interaction(method, pooling,package),
                     shape=interaction(method, pooling,package))) +
  facet_wrap(~parameter, ncol=6)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2.5) +  
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+ 
  labs(x='Model',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions Across Models: Q Parameters')+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  theme(text=element_text(size = 16))+
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))+
  coord_flip()
```

---

class: small, center


```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=12, fig.height=8.5}

params_r <- filter(pars, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8"))
ggplot(params_r, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color=model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1))+ 
  labs(x='Analysis approach', y='Estimate', color='Model',shape='Model', title='Estimates of R Parameters Across Models')+
  theme_bw() + 
  theme(text=element_text(size = 16))+
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))+
  coord_flip()
```


---

class: small, center


```{r, echo = FALSE, warning=FALSE, fig.width=12, fig.height=8.5}
params_r <- filter(res_between, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8"))
ggplot(params_r, aes(y = est_diff, x = model,
                     col=interaction(method, pooling,package),
                     shape=interaction(method, pooling,package))) +
  facet_wrap(~parameter, ncol=6)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2.5) + 
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+ 
  labs(x='Model',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions Across Models: R Parameters')+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  theme(text=element_text(size = 16))+
  theme(plot.title=element_text(face = 'bold',size=16, hjust = 0.5))+
  coord_flip()
```

---

class: small

### References 
- Bröder, A., Kellen, D., Schütz, J., & Rohrmeier, C. (1613). Validating a two-high-threshold measurement model for confidence rating data in recognition. *Memory*, 21(8), 916–944. https://doi.org/10.1080/09658211.2013.767348
- Dube, C., Starns, J. J., Rotello, C. M., & Ratcliff, R. (2012). Beyond ROC curvature: Strength effects and response time data support continuous-evidence models of recognition memory. *Journal of Memory and Language*, 67(3), 389–406. https://doi.org/10.1016/j.jml.2012.06.002
- Jaeger, A., Cox, J. C., & Dobbins, I. G. (2012). Recognition confidence under violated and confirmed memory expectations. *Journal of Experimental Psychology: General*, 141(2), 282–301. https://doi.org/10.1037/a0025687
- Koen, J. D., Aly, M., Wang, W.-C., & Yonelinas, A. P. (2013). Examining the causes of memory strength variability: Recollection, attention failure, or encoding variability? *Journal of Experimental Psychology: Learning, Memory, and Cognition*, 39(6), 1726–1741. https://doi.org/10.1037/a0033671
- Steegen, S., Tuerlinckx, F., Gelman, A., & Vanpaemel, W. (2016). Increasing Transparency Through a Multiverse Analysis. *Perspectives on Psychological Science*, 11(5), 702–712. https://doi.org/10.1177/1745691616658637
