---
title: "A Multiverse Pipeline for MPT models "
subtitle: "Applications to Recognition Memory"
author: "Henrik Singmann (Twitter: <a href='https://twitter.com/HenrikSingmann'>@HenrikSingmann</a>)<br/>Georgia Eleni Kapetaniou (kapetaniou.el@gmail.com)<br/>University of Zurich<br/>https://github.com/singmann/mptmultiverse-2htm"
date: "April 2018"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "my-theme.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# see: https://github.com/yihui/xaringan
# install.packages("xaringan")
# see: 
# https://github.com/yihui/xaringan/wiki
# https://github.com/gnab/remark/wiki/Markdown
options(width=110)
options(digits = 4)
library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../../scripts/auxiliary_functions.R")
source("../../scripts/summary_plots.R")
load("../../broeder_exp1/model_orig.eqn-exp1.txt.RData")
results1 <- results

load("../../broeder_exp1/model_orig_qrest.eqn-exp1.txt.RData")
results2 <- results

load("../../broeder_exp1/model_orig_rrest.eqn-exp1.txt.RData")
results3 <- results
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

load("../../koen2010/koen2010_orig.eqn-Koen_2010_pure.csv.RData")
results1_2 <- results

load("../../koen2010/koen2010_qrest.eqn-Koen_2010_pure.csv.RData")
results2_2 <- results

load("../../koen2010/koen2010_rrest.eqn-Koen_2010_pure.csv.RData")
results3_2 <- results


load("../../koen2011/koen2011_orig.eqn-Koen_2011.csv.RData")
results1_3 <- results

load("../../koen2011/koen2011_qrest.eqn-Koen_2011.csv.RData")
results2_3 <- results

load("../../koen2011/koen2011_rrest.eqn-Koen_2011.csv.RData")
results3_3 <- results


load("../../koen2013full/koen2013f_orig.eqn-Koen-2013_full.csv.RData")
results1_4 <- results

load("../../koen2013full/koen2013f_qrest.eqn-Koen-2013_full.csv.RData")
results2_4 <- results

load("../../koen2013full/koen2013f_rrest.eqn-Koen-2013_full.csv.RData")
results3_4 <- results


load("../../pratte2010/pratte_orig.eqn-Pratte_2010.csv.RData")
results1_5 <- results

load("../../pratte2010/pratte_qrest.eqn-Pratte_2010.csv.RData")
results2_5 <- results

load("../../pratte2010/pratte_rrest.eqn-Pratte_2010.csv.RData")
results3_5 <- results


load("../../smith2004/smith_orig.eqn-Smith_2004.csv.RData")
results1_6 <- results

load("../../smith2004/smith_qrest.eqn-Smith_2004.csv.RData")
results2_6 <- results

load("../../smith2004/smith_rrest.eqn-Smith_2004.csv.RData")
results3_6 <- results

load("../../jang2009/jang_orig.eqn-Jang_2009.csv.RData")
results1_7 <- results

load("../../jang2009/jang_qrest.eqn-Jang_2009.csv.RData")
results2_7 <- results

load("../../jang2009/jang_rrest.eqn-Jang_2009.csv.RData")
results3_7 <- results


load("../../dube2012p/dubep_orig.eqn-Dube_2012-P.csv.RData")
results1_8 <- results

load("../../dube2012p/dubep_qrest.eqn-Dube_2012-P.csv.RData")
results2_8 <- results

load("../../dube2012p/dubep_rrest.eqn-Dube_2012-P.csv.RData")
results3_8 <- results


load("../../dube2012w/dubew_orig.eqn-Dube_2012-W.csv.RData")
results1_9 <- results

load("../../dube2012w/dubeW_qrest.eqn-Dube_2012-W.csv.RData")
results2_9 <- results

load("../../dube2012w/dubeW_rrest.eqn-Dube_2012-W.csv.RData")
results3_9 <- results


load("../../heathcote2006e1/heathcote_orig.eqn-Heathcote_2006_e1.csv.RData")
results1_10 <- results

load("../../heathcote2006e1/heathcote_qrest.eqn-Heathcote_2006_e1.csv.RData")
results2_10 <- results

load("../../heathcote2006e1/heathcote_rrest.eqn-Heathcote_2006_e1.csv.RData")
results3_10 <- results


load("../../heathcote2006e2/heathcote2_orig.eqn-Heathcote_2006_e2.csv.RData")
results1_11 <- results

load("../../heathcote2006e2/heathcote2_qrest.eqn-Heathcote_2006_e2.csv.RData")
results2_11 <- results

load("../../heathcote2006e2/heathcote2_rrest.eqn-Heathcote_2006_e2.csv.RData")
results3_11 <- results


load("../../jaeger2012/jaeger_orig.eqn-Jaeger_2012.csv.RData")
results1_12 <- results

load("../../jaeger2012/jaeger_qrest.eqn-Jaeger_2012.csv.RData")
results2_12 <- results

load("../../jaeger2012/jaeger_rrest.eqn-Jaeger_2012.csv.RData")
results3_12 <- results

load("../../koen2013/koen_orig.eqn-Koen_2013_immediate.csv.RData")
results1_13 <- results

load("../../koen2013/koen_qrest.eqn-Koen_2013_immediate.csv.RData")
results2_13 <- results

load("../../koen2013/koen_rrest.eqn-Koen_2013_immediate.csv.RData")
results3_13 <- results

gof_a <- bind_rows(
  unnest(results1_2, gof),
  unnest(results2_2, gof),
  unnest(results3_2, gof),
  unnest(results1_3, gof),
  unnest(results2_3, gof),
  unnest(results3_3, gof),
  unnest(results1_4, gof),
  unnest(results2_4, gof),
  unnest(results3_4, gof),
  unnest(results1_5, gof),
  unnest(results2_5, gof),
  unnest(results3_5, gof),
  unnest(results1_6, gof),
  unnest(results2_6, gof),
  unnest(results3_6, gof),
  unnest(results1_7, gof),
  unnest(results2_7, gof),
  unnest(results3_7, gof),
  unnest(results1_8, gof),
  unnest(results2_8, gof),
  unnest(results3_8, gof),
  unnest(results1_9, gof),
  unnest(results2_9, gof),
  unnest(results3_9, gof),
  unnest(results1_10, gof),
  unnest(results2_10, gof),
  unnest(results3_10, gof),
  unnest(results1_11, gof),
  unnest(results2_11, gof),
  unnest(results3_11, gof),
  unnest(results1_12, gof),
  unnest(results2_12, gof),
  unnest(results3_12, gof),
  unnest(results1_13, gof),
  unnest(results2_13, gof),
  unnest(results3_13, gof),
)

gof_a$pooling <- factor(gof_a$pooling, levels = c("no", "complete",  "partial"), 
                        labels = c("No", "Comp", "PP"))

gof_a$package <- factor(gof_a$package, levels = c("MPTinR", "TreeBUGS"), 
                        labels = c("MR", "TB"))
gof_a$method <- factor(gof_a$method, levels = c("PB/MLE", "asymptotic", "simple",
                                                "trait", "trait_uncorrelated","beta"), 
                       labels = c("PB", "asy", "ss", "trait", "trait_u","beta"))

gof_a$inter <- with(gof_a, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(gof_a$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                         "Comp.Bayes", "Trait.PP", "Trait_u.PP","Beta.PP")

gof_a$focus <- factor(gof_a$focus, levels = c('cov', 'mean'),
                      labels = c('Covariance', 'Mean'))

gof_a$model <- ifelse(gof_a$model=="jang_orig.eqn"|gof_a$model=="koen2010_orig.eqn"|gof_a$model=="koen2011_orig.eqn"|gof_a$model=="koen2013f_orig.eqn"|gof_a$model=="pratte_orig.eqn"|gof_a$model=="smith_orig.eqn"|gof_a$model=="dubep_orig.eqn"|gof_a$model=="jaeger_orig.eqn"|gof_a$model=="koen_orig.eqn"|gof_a$model=="koen_orig.eqn"|gof_a$model=="koen_orig.eqn"|gof_a$model=="heathcote_orig.eqn"|gof_a$model=="heathcote_orig.eqn"|gof_a$model=="dubew_orig.eqn"|gof_a$model=="heathcote2_orig.eqn"|gof_a$model=="koen_orig.eqn",
                      'Q & R Restr.',
                      ifelse(gof_a$model=="jang_qrest.eqn"|gof_a$model=="koen2010_qrest.eqn"|gof_a$model=="koen2011_qrest.eqn"|gof_a$model=="koen2013f_qrest.eqn"|gof_a$model=="pratte_qrest.eqn"|gof_a$model=="smith_qrest.eqn"|gof_a$model=="dubep_qrest.eqn"|gof_a$model=="jaeger_qrest.eqn"|gof_a$model=="koen_qrest.eqn"|gof_a$model=="heathcote_qrest.eqn"|gof_a$model=="dubew_qrest.eqn"|gof_a$model=="heathcote2_qrest.eqn"|gof_a$model=="koen_qrest.eqn",
                             'Q Restricted',
                             ifelse(gof_a$model=="jang_rrest.eqn"|gof_a$model=="koen2010_rrest.eqn"|gof_a$model=="koen2011_rrest.eqn"|gof_a$model=="koen2013f_rrest.eqn"|gof_a$model=="pratte_rrest.eqn"|gof_a$model=="smith_rrest.eqn"|gof_a$model=="dubep_rrest.eqn"|gof_a$model=="jaeger_rrest.eqn"|gof_a$model=="koen_rrest.eqn"|gof_a$model=="heathcote_rrest.eqn"|gof_a$model=="dubew_rrest.eqn"|gof_a$model=="heathcote2_rrest.eqn"|gof_a$model=="koen_rrest.eqn",
                                    'R Restricted',
                                    gof_a$model)))

gof_a$dataset <- factor(gof_a$dataset, levels = c("Jang_2009.csv", "Koen_2010_pure.csv", "Koen_2011.csv", "Koen-2013_full.csv", "Pratte_2010.csv", "Smith_2004.csv", "Dube_2012-P.csv", "Dube_2012-W.csv", "Heathcote_2006_e1.csv", "Heathcote_2006_e2.csv", "Jaeger_2012.csv", "Koen_2013_immediate.csv"), 
                        labels = c("Jang9", "Koen10", "Koen11","Koen13F","Pratte10","Smith4", "Dube12P", "Dube12W","Heath6-1","Heath6-2","Jae12","Koen13I"))


gof_all <- filter(gof_a, focus %in% c("Mean"))
ggplot(gof_all, aes(y = p, 
                    x = inter, col=dataset)) + 
  geom_point(size=5) +  
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~model,ncol = 3) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0", "0.5", "1")) +
  labs(x='Analysis approach',y= expression(italic(p)), 
       color='Data set', title='Goodness of fit')+
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))

```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
params <- bind_rows(
  unnest(results1_8, est_group),
  unnest(results2_8, est_group),
  unnest(results3_8, est_group),
  unnest(results1_9, est_group),
  unnest(results2_9, est_group),
  unnest(results3_9, est_group),
  unnest(results1_10, est_group),
  unnest(results2_10, est_group),
  unnest(results3_10, est_group),
  unnest(results1_11, est_group),
  unnest(results2_11, est_group),
  unnest(results3_11, est_group),
  unnest(results1_12, est_group),
  unnest(results2_12, est_group),
  unnest(results3_12, est_group),
  unnest(results1_13, est_group),
  unnest(results2_13, est_group),
  unnest(results3_13, est_group),
)

params$pooling <- factor(params$pooling, levels = c("no", "complete",  "partial"), 
                         labels = c("No", "Comp", "PP"))

params$package <- factor(params$package, levels = c("MPTinR", "TreeBUGS"), 
                         labels = c("MR", "TB"))
params$method <- factor(params$method, levels = c("PB/MLE", "asymptotic", "simple",
                                                  "trait", "trait_uncorrelated","beta"), 
                        labels = c("PB", "asy", "ss", "trait", "trait_u","beta"))

params$inter <- with(params, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(params$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                          "Comp.Bayes", "Trait.PP", "Trait_u.PP","Beta.PP")

params$model <- ifelse(params$model=="dubep_orig.eqn"|params$model=="jaeger_orig.eqn"|params$model=="koen_orig.eqn"|params$model=="koen_orig.eqn"|params$model=="koen_orig.eqn"|params$model=="heathcote_orig.eqn"|params$model=="heathcote_orig.eqn"|params$model=="dubew_orig.eqn"|params$model=="heathcote2_orig.eqn"|params$model=="koen_orig.eqn",
                       'Q & R Restr.',
                       ifelse(params$model=="dubep_qrest.eqn"|params$model=="jaeger_qrest.eqn"|params$model=="koen_qrest.eqn"|params$model=="heathcote_qrest.eqn"|params$model=="dubew_qrest.eqn"|params$model=="heathcote2_qrest.eqn"|params$model=="koen_qrest.eqn",
                              'Q Restricted',
                              ifelse(params$model=="dubep_rrest.eqn"|params$model=="jaeger_rrest.eqn"|params$model=="koen_rrest.eqn"|params$model=="heathcote_rrest.eqn"|params$model=="dubew_rrest.eqn"|params$model=="heathcote2_rrest.eqn"|params$model=="koen_rrest.eqn",
                                     'R Restricted',
                                     params$model)))

params$dataset <- factor(params$dataset, levels = c("Dube_2012-P.csv", "Dube_2012-W.csv", "Heathcote_2006_e1.csv", "Heathcote_2006_e2.csv", "Jaeger_2012.csv", "Koen_2013_immediate.csv"), 
                        labels = c("Dube12P", "Dube12W","Heath6-1","Heath6-2","Jae12","Koen13I"))


shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .9)

Core_all <- filter(params, parameter %in% c("Dn","Do","g") & model %in% c('R Restricted'))
ggplot(Core_all, aes(y = est, x = dataset,
                     color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=3) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Data set', y='Estimate', color='Analysis approach', shape='Analysis approach', title='Core Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
params_1 <- bind_rows(
  unnest(results1_2, est_group),
  unnest(results2_2, est_group),
  unnest(results3_2, est_group),
  unnest(results1_3, est_group),
  unnest(results2_3, est_group),
  unnest(results3_3, est_group),
  unnest(results1_4, est_group),
  unnest(results2_4, est_group),
  unnest(results3_4, est_group),
  unnest(results1_5, est_group),
  unnest(results2_5, est_group),
  unnest(results3_5, est_group),
  unnest(results1_6, est_group),
  unnest(results2_6, est_group),
  unnest(results3_6, est_group),
  unnest(results1_7, est_group),
  unnest(results2_7, est_group),
  unnest(results3_7, est_group),
)

params_1$pooling <- factor(params_1$pooling, levels = c("no", "complete",  "partial"), 
                         labels = c("No", "Comp", "PP"))

params_1$package <- factor(params_1$package, levels = c("MPTinR", "TreeBUGS"), 
                         labels = c("MR", "TB"))
params_1$method <- factor(params_1$method, levels = c("PB/MLE", "asymptotic", "simple",
                                                  "trait", "trait_uncorrelated","beta"), 
                        labels = c("PB", "asy", "ss", "trait", "trait_u","beta"))

params_1$inter <- with(params_1, interaction(method, pooling, package, drop = TRUE, sep = " "))
levels(params_1$inter) <- c("No.PB", "No.asy", "Comp.asy", "No.Bayes", 
                          "Comp.Bayes", "Trait.PP", "Trait_u.PP","Beta.PP")

params_1$model <- ifelse(params_1$model=="jang_orig.eqn"|params_1$model=="koen2010_orig.eqn"|params_1$model=="koen2011_orig.eqn"|params_1$model=="koen2013f_orig.eqn"|params_1$model=="pratte_orig.eqn"|params_1$model=="smith_orig.eqn",
                       'Q & R Restr.',
                       ifelse(params_1$model=="jang_qrest.eqn"|params_1$model=="koen2010_qrest.eqn"|params_1$model=="koen2011_qrest.eqn"|params_1$model=="koen2013f_qrest.eqn"|params_1$model=="pratte_qrest.eqn"|params_1$model=="smith_qrest.eqn",
                              'Q Restricted',
                              ifelse(params_1$model=="jang_rrest.eqn"|params_1$model=="koen2010_rrest.eqn"|params_1$model=="koen2011_rrest.eqn"|params_1$model=="koen2013f_rrest.eqn"|params_1$model=="pratte_rrest.eqn"|params_1$model=="smith_rrest.eqn",
                                     'R Restricted',
                                     params_1$model)))
params_1$dataset <- factor(params_1$dataset, levels = c("Jang_2009.csv", "Koen_2010_pure.csv", "Koen_2011.csv", "Koen-2013_full.csv", "Pratte_2010.csv", "Smith_2004.csv"), 
                        labels = c("Jang9", "Koen10", "Koen11","Koen13F","Pratte10","Smith4"))

Core_all <- filter(params_1, parameter %in% c("Dn","Do","g") & model %in% c('R Restricted'))
ggplot(Core_all, aes(y = est, x = dataset,
                     color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=3) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Data set', y='Estimate', color='Analysis approach', shape='Analysis approach', title='Core Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()


```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

Q_all <- filter(params, parameter %in% c("q_1", "q_2", "q_5", "q_6") & model %in% c('R Restricted'))
ggplot(Q_all, aes(y = est, x = dataset,
                  color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Data set', y='Estimate', color='Analysis approach', shape='Analysis approach', title='Q Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
Q_all <- filter(params_1, parameter %in% c("q_1", "q_2", "q_5", "q_6") & model %in% c('R Restricted'))
ggplot(Q_all, aes(y = est, x = dataset,
                  color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Data set', y='Estimate', color='Analysis approach', shape='Analysis approach', title='Q Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}
R_all <- filter(params, parameter %in% c("r_1", "r_2", "r_6") & model %in% c('R Restricted'))
ggplot(R_all, aes(y = est, x = dataset,
                  color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Data set', y='Estimate', color='Analysis approach', shape='Analysis approach', title='R Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small, center

```{r, echo = FALSE, warning=FALSE, fig.width=11, fig.height=6.5, dpi = 500, message=FALSE}

R_all <- filter(params_1, parameter %in% c("r_1", "r_2", "r_6") & model %in% c('R Restricted'))
ggplot(R_all, aes(y = est, x = dataset,
                  color=inter, shape=inter)) +
  facet_wrap( ~parameter, ncol=4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.6)+
  geom_point(position = dd, size = 3.5) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1), 
                     labels = c("0","0.5", "1")) + 
  labs(x='Data set', y='Estimate', color='Analysis approach', shape='Analysis approach', title='R Parameters Across Data sets for R Restricted')+
  theme_bw() + 
  theme(text=element_text(size = 24))+
  theme(plot.title=element_text(face = 'bold',size=24, hjust = 0.5))+
  coord_flip()
```

---

class: small

### References 
- Bröder, A., Kellen, D., Schütz, J., & Rohrmeier, C. (2013). Validating a two-high-threshold measurement model for confidence rating data in recognition. *Memory*, 21(8), 916-944. https://doi.org/10.1080/09658211.2013.767348
- Dube, C., Starns, J. J., Rotello, C. M., & Ratcliff, R. (2012). Beyond ROC curvature: Strength effects and response time data support continuous-evidence models of recognition memory. *Journal of Memory and Language*, 67(3), 389-406. https://doi.org/10.1016/j.jml.2012.06.002
- Jaeger, A., Cox, J. C., & Dobbins, I. G. (2012). Recognition confidence under violated and confirmed memory expectations. *Journal of Experimental Psychology: General*, 141(2), 282-301. https://doi.org/10.1037/a0025687
- Koen, J. D., Aly, M., Wang, W.-C., & Yonelinas, A. P. (2013). Examining the causes of memory strength variability: Recollection, attention failure, or encoding variability? *Journal of Experimental Psychology: Learning, Memory, and Cognition*, 39(6), 1726-1741. https://doi.org/10.1037/a0033671
- Steegen, S., Tuerlinckx, F., Gelman, A., & Vanpaemel, W. (2016). Increasing Transparency Through a Multiverse Analysis. *Perspectives on Psychological Science*, 11(5), 702-712. https://doi.org/10.1177/1745691616658637
