
---
title: "Heathcote 2006_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../scripts/auxiliary_functions.R")
source("../scripts/summary_plots.R")

load("heathcote_orig.eqn-Heathcote_2006_e1.csv.RData")
results1 <- results

load("heathcote_qrest.eqn-Heathcote_2006_e1.csv.RData")
results2 <- results

load("heathcote_rrest.eqn-Heathcote_2006_e1.csv.RData")
results3 <- results
```

###Experiment summary

The aim of the experiment was to test the main effects of frequency and density separately for each factor keeping the other controlled. The stimuli were words of varying frequency (high-low) and neighborhood-density (high-low) forming 4 categories. 16 subjects participated in 8 study and test cycles, where 560 words were randomly allocated to seven study test lists of equal length. For each list, half of the words were allocated to the study task and the other half were presented as new during the test phase. The study phase included 40 words, 10 from each category, and the test phase includies the studied items and an equal number of new words. The participants were informed that they would view lists of words then subsequently be presented with a list containing both old and new words. They were instructed to indicate whether each word during the test phase was old or new and to rate their confidence on a 3 point scale. The six possible responses were sure old, probably old, possibly old, possibly new, probably new, and sure new. Participants were reminded to make use of all six response categories in the recognition memory tests.

### Some information on the models

**Model Original:** q_2 = q_5, & r_2 = r_5 (all but highest confidence response mapping of uncertainty and detection states equated)  
**Q restricted:** q_2 = q_5 (all but highest confidence response mapping of uncertainty states equated)  
**R restricted:** r_2 = r_5 (all but highest confidence response mapping of detection states equated)  

### Some information on convergence

#### For Model Original
One approach failed:
partial, TreeBUGS, beta

Frequentist approach with no pooling (asymptotic.no.MPTinR) had 0.125 as proportion of participants with non-identified parameters.
Frequentist approach with complete pooling (asymptotic.complete.MPTinR) had no convergence problems.  

Bayesian approach with no pooling (simple.no.TreeBUGS) had 4 parameters with Rhat > 1.05 and with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs and trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05.  

#### For Q restricted
One approach failed:
partial, TreeBUGS, beta

Frequentist approach with no pooling (asymptotic.no.MPTinR) had 0.625 as proportion of participants with non-identified parameters.
Frequentist approach with complete pooling (asymptotic.complete.MPTinR) had some convergence problems:  
rank.fischer = 4, n.parameters = 10, convergence = 0.  

Bayesian approach with no pooling (simple.no.TreeBUGS) and with complete pooling (simple.complete.TreeBUGS) both converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs and trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05. 

#### For R restricted
Frequentist approach with no pooling (asymptotic.no.MPTinR) had 0.250 as proportion of participants with non-identified parameters.
Frequentist approach with complete pooling (asymptotic.complete.MPTinR) had no convergence problems.  

Bayesian approach with no pooling (simple.no.TreeBUGS) and with complete pooling (simple.complete.TreeBUGS) both converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs, trait_uncorrelated.partial.TreeBUGS and beta.partial.Treebugs) converged well, all Rhat < 1.05. 

### Parameter estimation

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=7} 
pars <- bind_rows(unnest(results1, est_group))

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

ggplot(pars,aes(y = est, x = parameter, 
                col=interaction(method, pooling,package),
                shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Original Model')+
  scale_shape_manual(values=shapes) +
  theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```

**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=7}
pars <- bind_rows(unnest(results2, est_group))

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))


ggplot(pars,aes(y = est, x = parameter, 
                col=interaction(method, pooling,package),
                shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Q Restricted')+
  scale_shape_manual(values=shapes) +
  theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=7}
pars <- bind_rows(unnest(results3, est_group))

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))


ggplot(pars,aes(y = est, x = parameter, 
                col=interaction(method, pooling,package),
                shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for R Restricted')+
  scale_shape_manual(values=shapes) +
  theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**Core parameters**
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
pars <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

pars$pooling <- ifelse(pars$pooling=="no",
                       'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                       'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                      'PB',
                      ifelse(pars$method=="asymptotic",
                             'asy',
                             ifelse(pars$method=="simple",
                                    '',
                                    ifelse(pars$method=="trait",
                                           'trait',
                                           ifelse(pars$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))

pars$model <- ifelse(pars$model=='heathcote_orig.eqn',
                     'Original Model',
                     ifelse(pars$model=='heathcote_qrest.eqn',
                            'Q Restricted',
                            'R Restricted'))

core <- filter(pars, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est, x = model,
                 col=interaction(method, pooling,package),
                 shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() +
  facet_wrap(~parameter) +
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()


ggplot(core, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_wrap(~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Core Parameters Across Models')+
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
```
**Q parameters**

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=8}
params_q <- filter(pars, parameter %in% c("q_1", "q_2", "q_5", "q_6"))
ggplot(params_q, aes(y = est, x = model,
                     col=interaction(method, pooling,package),
                     shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  facet_wrap(~parameter, ncol = 4) +
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()

ggplot(params_q, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_wrap(~parameter, ncol = 4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
  labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of Q Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
```
**R parameters**

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=8}
params_r <- filter(pars, parameter %in% c("r_1", "r_2", "r_5", "r_6"))
ggplot(params_r, aes(y = est, x = model,
                     col=interaction(method, pooling,package),
                     shape=interaction(method, pooling,package))) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  facet_wrap(~parameter, ncol=4) +
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of R Parameters Across Models')+
  theme_bw() +
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()

ggplot(params_r, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
 facet_wrap(~parameter, ncol = 4) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_shape_manual(values=shapes) +
   scale_y_continuous(breaks=seq(0,1,by=.25),limits=c(0,1))+ 
   labs(x='Analysis approach',y='Estimate', color='Model',shape='Model', title='Estimates of R Parameters Across Models')+
  theme_bw() + 
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
```

### Goodness of fit

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results1, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                      'No',
                      ifelse(gof$pooling=="complete",
                             'Comp',
                             'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                      'MR',
                      'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                     'PB',
                     ifelse(gof$method=="asymptotic",
                            'asy',
                            ifelse(gof$method=="simple",
                                   '',
                                   ifelse(gof$method=="trait",
                                          'trait',
                                          ifelse(gof$method=="trait_uncorrelated",
                                                 'trait_u',
                                                 'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                    'Mean',
                    ifelse(gof$focus=="cov",
                           'Covariance',
                           gof$focus))


ggplot(gof, aes(y = p, 
                x = interaction(method, pooling, package))) + 
  geom_point(size=2) + ylim(0, 1) + 
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  labs(x='Analysis approach',y='p value', title='Goodness of fit: Original model')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```
**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results2, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                      'No',
                      ifelse(gof$pooling=="complete",
                             'Comp',
                             'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                      'MR',
                      'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                     'PB',
                     ifelse(gof$method=="asymptotic",
                            'asy',
                            ifelse(gof$method=="simple",
                                   '',
                                   ifelse(gof$method=="trait",
                                          'trait',
                                          ifelse(gof$method=="trait_uncorrelated",
                                                 'trait_u',
                                                'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                    'Mean',
                    ifelse(gof$focus=="cov",
                           'Covariance',
                           gof$focus))


ggplot(gof, aes(y = p, 
                x = interaction(method, pooling, package))) + 
  geom_point(size=2) + ylim(0, 1) + 
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  labs(x='Analysis approach',y='p value', title='Goodness of fit: Q restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results3, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                      'No',
                      ifelse(gof$pooling=="complete",
                             'Comp',
                             'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                      'MR',
                      'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                     'PB',
                     ifelse(gof$method=="asymptotic",
                            'asy',
                            ifelse(gof$method=="simple",
                                   '',
                                   ifelse(gof$method=="trait",
                                          'trait',
                                          ifelse(gof$method=="trait_uncorrelated",
                                                 'trait_u',
                                                'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                    'Mean',
                    ifelse(gof$focus=="cov",
                           'Covariance',
                           gof$focus))


ggplot(gof, aes(y = p, 
                x = interaction(method, pooling, package))) + 
  geom_point(size=2) + ylim(0, 1) + 
  geom_hline(yintercept = .05, lty = 2)+
  theme_bw() + coord_flip() +
  facet_wrap(~focus) +
  labs(x='Analysis approach',y='p value', title='Goodness of fit: R restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))

```
