---
title: "Broeder Experiment 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../scripts/auxiliary_functions.R")
source("../scripts/summary_plots.R")

load("model_orig_n.eqn-exp2.txt.RData")
```

### Some info on the models

**Model Original:** q_2 = q_7, q_3 = q_6 & r_3 = r_6 (all but highest confidence response mapping of uncertainty states equated and lowest two confidence response mapping of detection states equated)

### Some info on convergence

#### For Model Original

One approach failed:  
partial, TreeBUGS, beta  

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR). 
No identified parameters for no pooling?

Bayesian approach with no pooling (simple.no.TreeBUGS) had 1 parameter with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait_uncorrelated.partial.TreeBUGS) had 49 parameters with Rhat > 1.05 but uncorrelated (trait_uncorrelated.partial.TreeBUGS) had 4 parameters with Rhat > 1.05.  

### Parameter estimation

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=15, fig.height=12}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est <- unnest(results, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est)
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
tests <- unnest(results, est_group)

parameters_bn <- filter(par_est, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn","r_7_bn","r_8_bn"))

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

ggplot(parameters_bn, aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
tests <- unnest(results, est_group)

parameters_bo <- filter(par_est, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo","r_7_bo","r_8_bo"))

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

ggplot(parameters_bo, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
```

### Estimated differences

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=15, fig.height=12}
res_between <-  unnest(results, test_between) 

gg_est2 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2)
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results, test_between) 

parameters_bn <- filter(par_est, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn","r_7_bn","r_8_bn"))

gg_est2_bn <- ggplot(parameters_bn, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_bn)
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results, test_between) 

parameters_bo <- filter(par_est, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo","r_7_bo","r_8_bo"))

gg_est2_bo <- ggplot(parameters_bo, aes(y = est_diff, x = parameter, 
                                   col=interaction(method, pooling,package),
                                   shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_bo)
```

### Goodness of fit

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1 <-  unnest(results, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1)
```

### Goodness of fit per condition

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2 <- unnest(results, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2)
```
