---
title: "Broeder Experiment 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../scripts/auxiliary_functions.R")
source("../scripts/summary_plots.R")

load("model_orig_n.eqn-exp2.txt.RData")
results1 <- results

load("model_orig_n_qrest.eqn-exp2.txt.RData")
results2 <- results

load("model_orig_n_rrest.eqn-exp2.txt.RData")
results3 <- results
```

### Some info on the models

**Model Original:** q_2 = q_7, q_3 = q_6 & r_3 = r_6 (all but highest confidence response mapping of uncertainty states equated and lowest two confidence response mapping of detection states equated)  
**Q restricted:** q_2 = q_7, q_3 = q_6 (all but highest confidence response mapping of uncertainty states equated)  
**R restricted:** r_3 = r_6 (lowest two confidence response mapping of detection states equated) 

### Some info on convergence

#### For Model Original

One approach failed:  
partial, TreeBUGS, beta  

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR). 
No identified parameters for no pooling?

Bayesian approach with no pooling (simple.no.TreeBUGS) had 1 parameter with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling had 49 parameters with Rhat > 1.05 but uncorrelated (trait_uncorrelated.partial.TreeBUGS) had 4 parameters with Rhat > 1.05.  

#### For Q restricted

One approach failed:  
partial, TreeBUGS, beta  

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR). 

Bayesian approach with no pooling (simple.no.TreeBUGS) had 5 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs) had 89 parameters with Rhat > 1.05 but uncorrelated (trait_uncorrelated.partial.TreeBUGS) had 7 parameters with Rhat > 1.05.  

#### For R restricted

One approach failed:  
partial, TreeBUGS, beta  

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR). 

Bayesian approach with no pooling (simple.no.TreeBUGS) had 2 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait.partial.Treebugs) had 41 parameters with Rhat > 1.05 but uncorrelated (trait_uncorrelated.partial.TreeBUGS) had 5 parameters with Rhat > 1.05.  

### Parameter estimation

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=15, fig.height=12}

pars <- bind_rows(unnest(results1, est_group))
pars$condition <- ifelse(pars$condition=="strong_naming",
                                    'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                         'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                              'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                       'PB',
                       ifelse(pars$method=="asymptotic",
                              'asy',
                              ifelse(pars$method=="simple",
                                     '',
                                     ifelse(pars$method=="trait",
                                            'trait',
                                            ifelse(pars$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))


shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)


ggplot(pars, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Original Model')+
    theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=15, fig.height=12}
pars <- bind_rows(unnest(results2, est_group))
pars$condition <- ifelse(pars$condition=="strong_naming",
                                    'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                         'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                              'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                       'PB',
                       ifelse(pars$method=="asymptotic",
                              'asy',
                              ifelse(pars$method=="simple",
                                     '',
                                     ifelse(pars$method=="trait",
                                            'trait',
                                            ifelse(pars$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))

ggplot(pars, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Q restricted')+
    theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=15, fig.height=12}
pars <- bind_rows(unnest(results3, est_group))
pars$condition <- ifelse(pars$condition=="strong_naming",
                                    'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                         'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                              'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                       'PB',
                       ifelse(pars$method=="asymptotic",
                              'asy',
                              ifelse(pars$method=="simple",
                                     '',
                                     ifelse(pars$method=="trait",
                                            'trait',
                                            ifelse(pars$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))
ggplot(pars, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for R restricted')+
  theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
  
```

***Graphs per Bias Condition***

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
pas <- unnest(results1, est_group)

pars <- bind_rows(unnest(results1, est_group))
pars$condition <- ifelse(pars$condition=="strong_naming",
                                    'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                         'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                              'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                       'PB',
                       ifelse(pars$method=="asymptotic",
                              'asy',
                              ifelse(pars$method=="simple",
                                     '',
                                     ifelse(pars$method=="trait",
                                            'trait',
                                            ifelse(pars$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))


parameters_bn <- filter(pars, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn","r_7_bn","r_8_bn"))

ggplot(parameters_bn, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Original Model per condition')+
   theme_bw()+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
 
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
parameters_bo <- filter(pars, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo","r_7_bo","r_8_bo"))

ggplot(parameters_bo, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Original Model per condition')+
  theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
  
```

**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
pars <- unnest(results2, est_group)

pars$condition <- ifelse(pars$condition=="strong_naming",
                                    'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                         'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                              'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                       'PB',
                       ifelse(pars$method=="asymptotic",
                              'asy',
                              ifelse(pars$method=="simple",
                                     '',
                                     ifelse(pars$method=="trait",
                                            'trait',
                                            ifelse(pars$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))


parameters_bn <- filter(pars, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn",'r_6_bn',"r_7_bn","r_8_bn"))

ggplot(parameters_bn, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Q restricted per condition')+
   theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
 
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
parameters_bo <- filter(pars, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo",'r_6_bo',"r_7_bo","r_8_bo"))

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

ggplot(parameters_bo, aes(y = est,x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for Q restricted per condition')+
  theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
pars <- unnest(results3, est_group)

pars$condition <- ifelse(pars$condition=="strong_naming",
                                    'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                         'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                              'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                       'PB',
                       ifelse(pars$method=="asymptotic",
                              'asy',
                              ifelse(pars$method=="simple",
                                     '',
                                     ifelse(pars$method=="trait",
                                            'trait',
                                            ifelse(pars$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))


parameters_bn <- filter(pars, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn",'r_6_bn',"r_7_bn","r_8_bn"))

ggplot(parameters_bn, aes(y = est, x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for R restricted per condition')+
   theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
parameters_bo <- filter(pars, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo",'r_6_bo',"r_7_bo","r_8_bo"))

ggplot(parameters_bo, aes(y = est,x = parameter, 
                          col=interaction(method, pooling,package),
                          shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Parameter',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Estimation for R restricted per condition')+
   theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```
***Parameter comparison condition/bias***  
Core parameters

```{r, echo = FALSE, warning=FALSE, fig.width=12, fig.height=12}
pars <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

pars$condition <- ifelse(pars$condition=="strong_naming",
                                    'Strong wording',
                         'Weak wording'
)
pars$pooling <- ifelse(pars$pooling=="no",
                         'No',
                       ifelse(pars$pooling=="complete",
                              'Comp',
                              'PP'))
pars$package <- ifelse(pars$package=="MPTinR",
                       'MR',
                              'TB')

pars$method <- ifelse(pars$method=="PB/MLE",
                       'PB',
                       ifelse(pars$method=="asymptotic",
                              'asy',
                              ifelse(pars$method=="simple",
                                     '',
                                     ifelse(pars$method=="trait",
                                            'trait',
                                            ifelse(pars$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))
pars$model <- ifelse(pars$model=='model_orig_n.eqn',
                     'Original Model',
                     ifelse(pars$model=='model_orig_n_qrest.eqn',
                            'Q Restricted',
                            'R Restricted'))

core <- filter(pars, parameter %in% c("Do_bn", "Do_bo","Dn_bn", "Dn_bo","g_bn","g_bo"))
core <- add_column(core,bias=1)
core$bias <- ifelse(core$parameter=="Dn_bn",
                    'bn',
                    ifelse(core$parameter=="Do_bn",
                    'bn',
                    ifelse(core$parameter=='g_bn',
                           'bn',
                    'bo')))

core <- add_column(core,cp=1)
core$cp <- ifelse(core$parameter=="Dn_bn",
                    'Dn',
                    ifelse(core$parameter=="Do_bn",
                           'Do',
                           ifelse(core$parameter=='g_bn',
                                  'g',
                                  ifelse(core$parameter=="Dn_bo",
                                         'Dn',
                                         ifelse(core$parameter=='Do_bo',
                                                'Do',
                                                ifelse(core$parameter=='g_bo',
                                                       'g',
                                  core$parameter))))))



ggplot(core, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_grid(interaction(bias,condition) ~cp) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Core Parameters Across Models')+
  theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+ 
  coord_flip()
```
Q Parameters

```{r, echo = FALSE, warning=FALSE, fig.width=12, fig.height=12}

params_q <- filter(pars, parameter %in% c("q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn"))

params_q <- add_column(params_q,bias=1)
params_q$bias <- ifelse(params_q$parameter=="q_1_bn",
                    'bn',
                    ifelse(params_q$parameter=="q_2_bn",
                           'bn',
                           ifelse(params_q$parameter=="q_3_bn",
                                  'bn',
                                  ifelse(params_q$parameter=="q_6_bn",
                                         'bn',
                                         ifelse(params_q$parameter=="q_7_bn",
                                                'bn',
                                                ifelse(params_q$parameter=="q_8_bn",
                                                       'bn',
                                  'bo'))))))

params_q <- add_column(params_q,pq=1)
params_q$pq <- ifelse(params_q$parameter=="q_1_bn",
                  'q_1',
                  ifelse(params_q$parameter=="q_2_bn",
                         'q_2',
                         ifelse(params_q$parameter=="q_3_bn",
                                'q_3',
                                ifelse(params_q$parameter=="q_6_bn",
                                       'q_6',
                                       ifelse(params_q$parameter=="q_7_bn",
                                              'q_7',
                                              ifelse(params_q$parameter=="q_8_bn",
                                                     'q_8',
                                                     ifelse(params_q$parameter=="q_1_bo",
                                                            'q_1',
                                                            ifelse(params_q$parameter=="q_2_bo",
                                                                   'q_2',
                                                                   ifelse(params_q$parameter=="q_3_bo",
                                                                          'q_3',
                                                                          ifelse(params_q$parameter=="q_6_bo",
                                                                                 'q_6',
                                                                                 ifelse(params_q$parameter=="q_7_bo",
                                                                                        'q_7',
                                                                                        ifelse(params_q$parameter=="q_8_bo",
                                                                                               'q_8',
                                                     params_q$parameter))))))))))))

ggplot(params_q, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_grid(interaction(bias,condition) ~pq) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1))+ 
  scale_shape_manual(values=shapes) +
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of Q Parameters Across Models')+
  theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+ 
  coord_flip()
```
R parameters

```{r, echo = FALSE, warning=FALSE, fig.width=12, fig.height=12}

params_r <- filter(pars, parameter %in% c("r_1_bo","r_2_bo","r_3_bo",'r_6_bo',"r_7_bo","r_8_bo","r_1_bn","r_2_bn","r_3_bn",'r_6_bn',"r_7_bn","r_8_bn"))

params_r <- add_column(params_r,bias=1)
params_r$bias <- ifelse(params_r$parameter=="r_1_bn",
                        'bn',
                        ifelse(params_r$parameter=="r_2_bn",
                               'bn',
                               ifelse(params_r$parameter=="r_3_bn",
                                      'bn',
                                      ifelse(params_r$parameter=="r_6_bn",
                                      'bn',
                                             ifelse(params_r$parameter=="r_7_bn",
                                                    'bn',
                                                    ifelse(params_r$parameter=="r_8_bn",
                                                           'bn',
                                                           'bo'))))))

params_r <- add_column(params_r,pr=1)
params_r$pr <- ifelse(params_r$parameter=="r_1_bn",
                      'r_1',
                      ifelse(params_r$parameter=="r_2_bn",
                             'r_2',
                             ifelse(params_r$parameter=="r_3_bn",
                                    'r_3',
                                    ifelse(params_r$parameter=="r_6_bn",
                                    'r_6',
                                    ifelse(params_r$parameter=="r_7_bn",
                                                  'r_7',
                                                  ifelse(params_r$parameter=="r_8_bn",
                                                         'r_8',
                                                         ifelse(params_r$parameter=="r_1_bo",
                                                                'r_1',
                                                                ifelse(params_r$parameter=="r_2_bo",
                                                                       'r_2',
                                                                       ifelse(params_r$parameter=="r_3_bo",
                                                                              'r_3',
                                                                               ifelse(params_r$parameter=="r_6_bo",
                                                                              'r_6',
                                                                              ifelse(params_r$parameter=="r_7_bo",
                                                                                            'r_7',
                                                                                            ifelse(params_r$parameter=="r_8_bo",
                                                                                                   'r_8',
                                                                                                   params_r$parameter))))))))))))



ggplot(params_r, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_grid(interaction(bias,condition) ~pr) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1))+ 
  scale_shape_manual(values=shapes) +
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Estimates of R Parameters Across Models')+
  theme_bw()+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+ 
  coord_flip()
```

### Estimated differences

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results1, test_between) 

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'
res_between$pooling <- ifelse(res_between$pooling=="no",
                         'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                              'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                       'PB',
                       ifelse(res_between$method=="asymptotic",
                              'asy',
                              ifelse(res_between$method=="simple",
                                     '',
                                     ifelse(res_between$method=="trait",
                                            'trait',
                                            ifelse(res_between$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))


gg_est2_1 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: Original Model')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2_1)
```

**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results2, test_between) 

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'
res_between$pooling <- ifelse(res_between$pooling=="no",
                         'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                              'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                       'PB',
                       ifelse(res_between$method=="asymptotic",
                              'asy',
                              ifelse(res_between$method=="simple",
                                     '',
                                     ifelse(res_between$method=="trait",
                                            'trait',
                                            ifelse(res_between$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))

gg_est2_2 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: Q restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2_2)
```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results3, test_between) 

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'
res_between$pooling <- ifelse(res_between$pooling=="no",
                         'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                              'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                       'PB',
                       ifelse(res_between$method=="asymptotic",
                              'asy',
                              ifelse(res_between$method=="simple",
                                     '',
                                     ifelse(res_between$method=="trait",
                                            'trait',
                                            ifelse(res_between$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))

gg_est2_3 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: R restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2_3)
```

***Graphs per Bias Condition***

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results1, test_between) 

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'
res_between$pooling <- ifelse(res_between$pooling=="no",
                         'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                              'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                       'PB',
                       ifelse(res_between$method=="asymptotic",
                              'asy',
                              ifelse(res_between$method=="simple",
                                     '',
                                     ifelse(res_between$method=="trait",
                                            'trait',
                                            ifelse(res_between$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))

parameters_bn <- filter(res_between, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn","r_7_bn","r_8_bn"))

gg_est2_bn <- ggplot(parameters_bn, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: Original Model, bn')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2_bn)
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}

parameters_bo <- filter(res_between, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo","r_7_bo","r_8_bo"))

gg_est2_bo <- ggplot(parameters_bo, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: Original Model, bo')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2_bo)
```
**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results2, test_between) 

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'
res_between$pooling <- ifelse(res_between$pooling=="no",
                         'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                              'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                       'PB',
                       ifelse(res_between$method=="asymptotic",
                              'asy',
                              ifelse(res_between$method=="simple",
                                     '',
                                     ifelse(res_between$method=="trait",
                                            'trait',
                                            ifelse(res_between$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))

parameters_bn <- filter(res_between, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn",'r_6_bn',"r_7_bn","r_8_bn"))

gg_est2_bn <- ggplot(parameters_bn, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: Q restricted, bn')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2_bn)
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}

parameters_bo <- filter(res_between, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo",'r_6_bo',"r_7_bo","r_8_bo"))

gg_est2_bo <- ggplot(parameters_bo, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
   labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: Q restricted, bo')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2_bo)
```
**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results3, test_between) 

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'
res_between$pooling <- ifelse(res_between$pooling=="no",
                         'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                              'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                       'PB',
                       ifelse(res_between$method=="asymptotic",
                              'asy',
                              ifelse(res_between$method=="simple",
                                     '',
                                     ifelse(res_between$method=="trait",
                                            'trait',
                                            ifelse(res_between$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))

parameters_bn <- filter(res_between, parameter %in% c("Do_bn", "Dn_bn", "g_bn","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn","r_1_bn","r_2_bn","r_3_bn",'r_6_bn',"r_7_bn","r_8_bn"))

gg_est3_bn <- ggplot(parameters_bn, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
   labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: R restricted, bn')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est3_bn)
```
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}

parameters_bo <- filter(res_between, parameter %in% c("Do_bo", "Dn_bo", "g_bo","q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","r_1_bo","r_2_bo","r_3_bo",'r_6_bo',"r_7_bo","r_8_bo"))

gg_est3_bo <- ggplot(parameters_bo, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
   labs(x='Parameter',y='Estimated Difference', color='Analysis approach',shape='Analysis approach', title='Parameter Differences Between Conditions: R restricted, bn')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est3_bo)
```

***Parameter comparison condition/bias***  
Core parameters

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <- bind_rows(
  unnest(results1, test_between),
  unnest(results2, test_between),
  unnest(results3, test_between)
)

res_between$condition1 <- 'Strong wording'
res_between$condition2 <- 'Weak wording'
res_between$pooling <- ifelse(res_between$pooling=="no",
                         'No',
                       ifelse(res_between$pooling=="complete",
                              'Comp',
                              'PP'))
res_between$package <- ifelse(res_between$package=="MPTinR",
                       'MR',
                              'TB')

res_between$method <- ifelse(res_between$method=="PB/MLE",
                       'PB',
                       ifelse(res_between$method=="asymptotic",
                              'asy',
                              ifelse(res_between$method=="simple",
                                     '',
                                     ifelse(res_between$method=="trait",
                                            'trait',
                                            ifelse(res_between$method=="trait_uncorrelated",
                                                   'trait_u',
                                                   'beta')))))
res_between$model <- ifelse(res_between$model=='model_orig_n.eqn',
                     'Original Model',
                     ifelse(res_between$model=='model_orig_n_qrest.eqn',
                            'Q Restricted',
                            'R Restricted'))

core <- filter(res_between, parameter %in% c("Do_bn", "Do_bo","Dn_bn", "Dn_bo","g_bn","g_bo"))
core <- add_column(core,bias=1)
core$bias <- ifelse(core$parameter=="Dn_bn",
                    'bn',
                    ifelse(core$parameter=="Do_bn",
                           'bn',
                           ifelse(core$parameter=='g_bn',
                                  'bn',
                                  'bo')))

core <- add_column(core,cp=1)
core$cp <- ifelse(core$parameter=="Dn_bn",
                  'Dn',
                  ifelse(core$parameter=="Do_bn",
                         'Do',
                         ifelse(core$parameter=='g_bn',
                                'g',
                                ifelse(core$parameter=="Dn_bo",
                                       'Dn',
                                       ifelse(core$parameter=='Do_bo',
                                              'Do',
                                              ifelse(core$parameter=='g_bo',
                                                     'g',
                                                     core$parameter))))))


dd <- position_dodge(w = .75)
ggplot(core, aes(y = est_diff, x = interaction(method, pooling,package),
                  shape=model, color=model)) +
  facet_grid(bias ~cp)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Differences across conditions and models')+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
```

Q Parameters

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}

params_q <- filter(res_between, parameter %in% c("q_1_bo", "q_2_bo","q_3_bo","q_6_bo","q_7_bo","q_8_bo","q_1_bn", "q_2_bn","q_3_bn","q_6_bn","q_7_bn","q_8_bn"))

params_q <- add_column(params_q,bias=1)
params_q$bias <- ifelse(params_q$parameter=="q_1_bn",
                        'bn',
                        ifelse(params_q$parameter=="q_2_bn",
                               'bn',
                               ifelse(params_q$parameter=="q_3_bn",
                                      'bn',
                                      ifelse(params_q$parameter=="q_6_bn",
                                             'bn',
                                             ifelse(params_q$parameter=="q_7_bn",
                                                    'bn',
                                                    ifelse(params_q$parameter=="q_8_bn",
                                                           'bn',
                                                           'bo'))))))

params_q <- add_column(params_q,pq=1)
params_q$pq <- ifelse(params_q$parameter=="q_1_bn",
                      'q_1',
                      ifelse(params_q$parameter=="q_2_bn",
                             'q_2',
                             ifelse(params_q$parameter=="q_3_bn",
                                    'q_3',
                                    ifelse(params_q$parameter=="q_6_bn",
                                           'q_6',
                                           ifelse(params_q$parameter=="q_7_bn",
                                                  'q_7',
                                                  ifelse(params_q$parameter=="q_8_bn",
                                                         'q_8',
                                                         ifelse(params_q$parameter=="q_1_bo",
                                                                'q_1',
                                                                ifelse(params_q$parameter=="q_2_bo",
                                                                       'q_2',
                                                                       ifelse(params_q$parameter=="q_3_bo",
                                                                              'q_3',
                                                                              ifelse(params_q$parameter=="q_6_bo",
                                                                                     'q_6',
                                                                                     ifelse(params_q$parameter=="q_7_bo",
                                                                                            'q_7',
                                                                                            ifelse(params_q$parameter=="q_8_bo",
                                                                                                   'q_8',
                                                                                                   params_q$parameter))))))))))))

gg_est2 <- ggplot(params_q, aes(y = est_diff, x = interaction(method, pooling,package),
                                shape=model, color=model)) +
  facet_grid(bias ~pq) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + 
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+ 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Differences across conditions and models')+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est2)

```

R Parameters

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}

params_r <- filter(res_between, parameter %in% c("r_1_bo","r_2_bo","r_3_bo",'r_6_bo',"r_7_bo","r_8_bo","r_1_bn","r_2_bn","r_3_bn",'r_6_bn',"r_7_bn","r_8_bn"))

params_r <- add_column(params_r,bias=1)
params_r$bias <- ifelse(params_r$parameter=="r_1_bn",
                        'bn',
                        ifelse(params_r$parameter=="r_2_bn",
                               'bn',
                               ifelse(params_r$parameter=="r_3_bn",
                                      'bn',
                                      ifelse(params_r$parameter=="r_6_bn",
                                             'bn',
                                      ifelse(params_r$parameter=="r_7_bn",
                                             'bn',
                                             ifelse(params_r$parameter=="r_8_bn",
                                                    'bn',
                                                    'bo'))))))

params_r <- add_column(params_r,pr=1)
params_r$pr <- ifelse(params_r$parameter=="r_1_bn",
                      'r_1',
                      ifelse(params_r$parameter=="r_2_bn",
                             'r_2',
                             ifelse(params_r$parameter=="r_3_bn",
                                    'r_3',
                                    ifelse(params_r$parameter=="r_6_bn",
                                           'r_6',
                                           ifelse(params_r$parameter=="r_7_bn",
                                                  'r_7',
                                                  ifelse(params_r$parameter=="r_8_bn",
                                                         'r_8',
                                                         ifelse(params_r$parameter=="r_1_bo",
                                                                'r_1',
                                                                ifelse(params_r$parameter=="r_2_bo",
                                                                       'r_2',
                                                                       ifelse(params_r$parameter=="r_3_bo",
                                                                              'r_3',
                                                                              ifelse(params_r$parameter=="r_6_bo",
                                                                                     'r_6',
                                                                                     ifelse(params_r$parameter=="r_7_bo",
                                                                                            'r_7',
                                                                                            ifelse(params_r$parameter=="r_8_bo",
                                                                                                   'r_8',
                                                                                                   params_r$parameter))))))))))))

gg_est3 <- ggplot(params_r, aes(y = est_diff, x = interaction(method, pooling,package),
                                shape=model, color=model)) +
  facet_grid(bias ~pr) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + 
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+ 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  labs(x='Model',y='Estimate', color='Analysis approach',shape='Analysis approach', title='Parameter Differences across conditions and models')+
   theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))+
  coord_flip()
plot(gg_est3)
```

### Goodness of fit

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results1, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                       'No',
                       ifelse(gof$pooling=="complete",
                              'Comp',
                              'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                       'MR',
                       'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                      'PB',
                      ifelse(gof$method=="asymptotic",
                             'asy',
                             ifelse(gof$method=="simple",
                                    '',
                                    ifelse(gof$method=="trait",
                                           'trait',
                                           ifelse(gof$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                      'Mean',
                      ifelse(gof$focus=="cov",
                             'Covariance',
                             gof$focus))


ggplot(gof, aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    labs(x='Analysis approach',y='p value', title='Goodness of fit: Model Original')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results2, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                       'No',
                       ifelse(gof$pooling=="complete",
                              'Comp',
                              'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                       'MR',
                       'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                      'PB',
                      ifelse(gof$method=="asymptotic",
                             'asy',
                             ifelse(gof$method=="simple",
                                    '',
                                    ifelse(gof$method=="trait",
                                           'trait',
                                           ifelse(gof$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                      'Mean',
                      ifelse(gof$focus=="cov",
                             'Covariance',
                             gof$focus))


ggplot(gof, aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    labs(x='Analysis approach',y='p value', title='Goodness of fit: Q restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gof <- bind_rows(unnest(results3, gof))

gof$pooling <- ifelse(gof$pooling=="no",
                       'No',
                       ifelse(gof$pooling=="complete",
                              'Comp',
                              'PP'))
gof$package <- ifelse(gof$package=="MPTinR",
                       'MR',
                       'TB')

gof$method <- ifelse(gof$method=="PB/MLE",
                      'PB',
                      ifelse(gof$method=="asymptotic",
                             'asy',
                             ifelse(gof$method=="simple",
                                    '',
                                    ifelse(gof$method=="trait",
                                           'trait',
                                           ifelse(gof$method=="trait_uncorrelated",
                                                  'trait_u',
                                                  'beta')))))
gof$focus <- ifelse(gof$focus=="mean",
                      'Mean',
                      ifelse(gof$focus=="cov",
                             'Covariance',
                             gof$focus))
ggplot(gof, aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    labs(x='Analysis approach',y='p value', title='Goodness of fit: R restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

### Goodness of fit per condition

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gof_group <- bind_rows(unnest(results1, gof_group))

gof_group$pooling <- ifelse(gof_group$pooling=="no",
                      'No',
                      ifelse(gof_group$pooling=="complete",
                             'Comp',
                             'PP'))
gof_group$package <- ifelse(gof_group$package=="MPTinR",
                      'MR',
                      'TB')

gof_group$method <- ifelse(gof_group$method=="PB/MLE",
                     'PB',
                     ifelse(gof_group$method=="asymptotic",
                            'asy',
                            ifelse(gof_group$method=="simple",
                                   '',
                                   ifelse(gof_group$method=="trait",
                                          'trait',
                                          ifelse(gof_group$method=="trait_uncorrelated",
                                                 'trait_u',
                                                 'beta')))))
gof_group$focus <- ifelse(gof_group$focus=="mean",
                    'Mean',
                    ifelse(gof_group$focus=="cov",
                           'Covariance',
                           gof_group$focus))
gof_group$condition <- ifelse(gof_group$condition=="strong_naming",
                         'Strong wording',
                         'Weak wording'
)
ggplot(gof_group, aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    labs(x='Analysis approach',y='p value', title='Goodness of fit per condition: Model Original')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gof_group <- bind_rows(unnest(results2, gof_group))

gof_group$pooling <- ifelse(gof_group$pooling=="no",
                      'No',
                      ifelse(gof_group$pooling=="complete",
                             'Comp',
                             'PP'))
gof_group$package <- ifelse(gof_group$package=="MPTinR",
                      'MR',
                      'TB')

gof_group$method <- ifelse(gof_group$method=="PB/MLE",
                     'PB',
                     ifelse(gof_group$method=="asymptotic",
                            'asy',
                            ifelse(gof_group$method=="simple",
                                   '',
                                   ifelse(gof_group$method=="trait",
                                          'trait',
                                          ifelse(gof_group$method=="trait_uncorrelated",
                                                 'trait_u',
                                                 'beta')))))
gof_group$focus <- ifelse(gof_group$focus=="mean",
                    'Mean',
                    ifelse(gof_group$focus=="cov",
                           'Covariance',
                           gof_group$focus))
gof_group$condition <- ifelse(gof_group$condition=="strong_naming",
                         'Strong wording',
                         'Weak wording'
)
ggplot(gof_group, aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    labs(x='Analysis approach',y='p value', title='Goodness of fit per condition: Q restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```

**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gof_group <- bind_rows(unnest(results3, gof_group))

gof_group$pooling <- ifelse(gof_group$pooling=="no",
                      'No',
                      ifelse(gof_group$pooling=="complete",
                             'Comp',
                             'PP'))
gof_group$package <- ifelse(gof_group$package=="MPTinR",
                      'MR',
                      'TB')

gof_group$method <- ifelse(gof_group$method=="PB/MLE",
                     'PB',
                     ifelse(gof_group$method=="asymptotic",
                            'asy',
                            ifelse(gof_group$method=="simple",
                                   '',
                                   ifelse(gof_group$method=="trait",
                                          'trait',
                                          ifelse(gof_group$method=="trait_uncorrelated",
                                                 'trait_u',
                                                 'beta')))))
gof_group$focus <- ifelse(gof_group$focus=="mean",
                    'Mean',
                    ifelse(gof_group$focus=="cov",
                           'Covariance',
                           gof_group$focus))
gof_group$condition <- ifelse(gof_group$condition=="strong_naming",
                         'Strong wording',
                         'Weak wording'
)
ggplot(gof_group, aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    labs(x='Analysis approach',y='p value', title='Goodness of fit per condition: Q restricted')+
  theme(plot.title=element_text(face = 'bold',size=12, hjust = 0.5))
```