---
title: "Experiment 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../scripts/auxiliary_functions.R")
source("../scripts/summary_plots.R")

load("model_orig.eqn-exp1.txt.RData")
results1 <- results

load("model_orig_qrest.eqn-exp1.txt.RData")
results2 <- results

load("model_orig_rrest.eqn-exp1.txt.RData")
results3 <- results
```

### Some info on the models

**Model Original:** q_2 = q_7, q_3 = q_6 & r_3 = r_6 (all but highest confidence response mapping of uncertainty states equated and lowest two confidence response mapping of detection states equated)  
**Q restricted:** q_2 = q_7, q_3 = q_6 (all but highest confidence response mapping of uncertainty states equated)  
**R restricted:** r_3 = r_6 (lowest two confidence response mapping of detection states equated)  

### Some info on convergence

#### For Model Original

Two approaches failed:  
partial, TreeBUGS, trait  
partial, TreeBUGS, beta  

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR).  

Bayesian approach with no pooling (simple.no.TreeBUGS) had 3 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05.  

#### For Q restricted
One approach failed:
partial, TreeBUGS, beta

Bayesian approach with no pooling (simple.no.TreeBUGS) had 4 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) had 2 parameters with Rhat > 1.05.   
Bayesian approach with partial pooling had 53 parameters with Rhat > 1.05  but uncorrelated (trait_uncorrelated.partial.TreeBUGS) had one parameter with Rhat > 1.05.  

#### For R restricted
One approach failed:
partial, TreeBUGS, beta

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR).  

Bayesian approach with no pooling (simple.no.TreeBUGS) had 54 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.     
Bayesian approach with partial pooling had 8 parameters with Rhat > 1.05  but uncorrelated (trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05. 

### Parameter estimation

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est1 <- unnest(results1, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est1)
```
**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est2 <- unnest(results2, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est2)
```
**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est3 <- unnest(results3, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est3)
```

**Core parameters**
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
par_est <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

core <- filter(par_est, parameter %in% c("Do", "Dn", "g"))
ggplot(core, aes(y = est, x = interaction(method, pooling,package),
                 shape=model, color =model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + 
  coord_flip()
```
**Q parameters**

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=8}
par_est <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

params_q <- filter(par_est, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8"))
ggplot(params_q, aes(y = est, x = interaction(method, pooling,package),
                     shape=model, color =model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1))+
  theme_bw() + 
  coord_flip() 
```
**R parameters**

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=8}
par_est <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group)
)

shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

params_r <- filter(par_est, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8"))
ggplot(params_r, aes(y = est, x = interaction(method, pooling,package),
                     shape=model, color =model)) +
  facet_grid(condition ~parameter) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  scale_shape_manual(values=shapes) +
  scale_y_continuous(breaks=seq(0,1,by=.5),limits=c(0,1))+
  theme_bw() + 
  coord_flip()
```

### Estimated differences

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results1, test_between) 

gg_est2_1 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_1)
```
**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results2, test_between) 

gg_est2_2 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_2)
```
**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results3, test_between) 

gg_est2_3 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_3)
```
**Core parameters**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <- bind_rows(
  unnest(results1, test_between),
  unnest(results2, test_between),
  unnest(results3, test_between)
)
dd <- position_dodge(w = .75)
core2 <- filter(res_between, parameter %in% c("Do", "Dn", "g"))
ggplot(core2, aes(y = est_diff, x = interaction(method, pooling,package),
                  shape=model, color=model)) +
  facet_wrap(~parameter, ncol=3)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
```
**Q Parameters**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
params_q <- filter(res_between, parameter %in% c("q_1", "q_2", "q_3", "q_6", "q_7", "q_8"))
ggplot(params_q, aes(y = est_diff, x = interaction(method, pooling,package),
                  shape=model, color=model)) +
  facet_wrap(~parameter, ncol=6)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + 
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  coord_flip()
```
**R Parameters**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
params_r <- filter(res_between, parameter %in% c("r_1", "r_2", "r_3", "r_6", "r_7", "r_8"))
ggplot(params_r, aes(y = est_diff, x = interaction(method, pooling,package),
                     shape=model, color=model)) +
  facet_wrap(~parameter, ncol=6)+
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) +
  scale_y_continuous(breaks=seq(-1,1,by=1),limits=c(-1,1))+
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 3) +
  coord_flip()
```

### Goodness of fit

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1_1 <-  unnest(results1, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1_1)
```
**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1_2 <-  unnest(results2, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1_2)
```
**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1_3 <-  unnest(results3, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1_3)
```
### Goodness of fit per condition

**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2_1 <- unnest(results1, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2_1)
```
**Q restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2_2 <- unnest(results2, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2_2)
```
**R restricted**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2_3 <- unnest(results3, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2_3)
```
