---
title: "Broeder Experiment 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("tidyr")
library("dplyr")
library("tibble")
library("rlang")
library("reshape2")
library("ggplot2")
library("parallel")
library("MPTinR")
library("TreeBUGS")
library("runjags")
library("purrr")
library("readr")
library("broom") # for tidy
source("../scripts/auxiliary_functions.R")
source("../scripts/summary_plots.R")

load("model_1.eqn-exp1.txt.RData")
results1 <- results

load("model_2.eqn-exp1.txt.RData")
results2 <- results

load("model_3.eqn-exp1.txt.RData")
results3 <- results

load("model_orig.eqn-exp1.txt.RData")
results4 <- results

```

### Some info on the models

**Model 1:** r_1 = r_8 (highest confidence response mapping of detection states equated)  
**Model 2:** q_4 = q_5 (lowest confidence response mapping of uncertainty states equated)  
**Model 3:** r_1 = r_8 & q_4 = q_5 (highest confidence response mapping of detection states equated and lowest confidence response mapping of uncertainty states equated)  
**Model Original:** q_2 = q_7, q_3 = q_6 & r_3 = r_6 (all but highest confidence response mapping of uncertainty states equated and lowest two confidence response mapping of detection states equated)

### Some info on convergence

#### For Model 1

Two approaches failed:  
partial, TreeBUGS, trait  
partial, TreeBUGS, beta  

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR).

Bayesian approach with complete pooling Rhat < 1.05, therefore converged well (simple.complete.TreeBUGS).  
Bayesian approach with no pooling (simple.no.TreeBUGS) had 374 parameters with Rhat > 1.05.  
Bayesian approach with partial pooling (trait_uncorrelated.partial.TreeBUGS) had 58 parameters with Rhat > 1.05.  

#### For Model 2

One approach failed:  
partial, TreeBUGS, beta 

Frequentist approach with complete pooling (asymptotic.complete.MPTinR) had some convergence problems:  
  condition     rank.fisher n.parameters convergence  
1 aggregated             6          14          0  
2 strong_naming          6          14          0  
3 weak_naming            9          14          0  

Bayesian approach with no pooling (simple.no.TreeBUGS) had 7 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait) had 38 parameters with Rhat > 1.05, but uncorrelated (trait_uncorrelated.partial.TreeBUGS) converged well with all Rhat < 1.05.

#### For Model 3

One approach failed:  
partial, TreeBUGS, beta 

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR).

Bayesian approach with no pooling (simple.no.TreeBUGS) had 204 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait) had 259 parameters with Rhat > 1.05, but uncorrelated (trait_uncorrelated.partial.TreeBUGS) had one parameter with Rhat > 1.05.  

#### For Model Original

Two approaches failed:  
partial, TreeBUGS, trait  
partial, TreeBUGS, beta  

Frequentist approach with complete pooling had no convergence problems (asymptotic.complete.MPTinR).  

Bayesian approach with no pooling (simple.no.TreeBUGS) had 3 parameters with Rhat > 1.05.  
Bayesian approach with complete pooling (simple.complete.TreeBUGS) converged well, all Rhat < 1.05.  
Bayesian approach with partial pooling (trait_uncorrelated.partial.TreeBUGS) converged well, all Rhat < 1.05.  

### Parameter estimation

```{r}
par_est <- bind_rows(
  unnest(results1, est_group),
  unnest(results2, est_group),
  unnest(results3, est_group),
  unnest(results4, est_group)
  )
```


**Model 1**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est1 <- unnest(results1, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est1)
```

**Model 2**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est2 <- unnest(results2, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
  facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est2)
```
**Model 3**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est3 <- unnest(results3, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est3)
```
**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
shapes <- c(16, 18, 15, 1, 0, 8, 11, 12)
dd <- position_dodge(w = .75)

gg_est4 <- unnest(results4, est_group) %>%
  ggplot(aes(y = est, x = parameter, 
             col=interaction(method, pooling,package),
             shape=interaction(method, pooling,package))) +
   facet_wrap(~condition, ncol = 1) +
  geom_errorbar(aes(ymin = est-se, ymax = est+se), position = dd, 
                width = 0.4)+
  geom_point(position = dd, size = 2) + 
  ylim(0,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw()
plot(gg_est4)
```

### Estimated differences

**Model 1**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results1, test_between) 

gg_est2_1 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_1)

```
**Model 2**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results2, test_between) 

gg_est2_2 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_2)
```
**Model 3**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results3, test_between) 

gg_est2_3 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_3)
```
**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=8}
res_between <-  unnest(results4, test_between) 

gg_est2_4 <- ggplot(res_between, aes(y = est_diff, x = parameter, 
                                     col=interaction(method, pooling,package),
                                     shape=interaction(method, pooling,package))) +
  facet_grid(condition2~condition1) +
  geom_errorbar(aes(ymin = ci_0.025, ymax = ci_0.975), 
                position = dd, width = 0.5)+
  geom_point(position = dd, size=2) + ylim(-1,1) + 
  scale_shape_manual(values=shapes) +
  theme_bw() + geom_hline(yintercept = 0, lty = 2) +
  coord_flip()
plot(gg_est2_4)
```

### Goodness of fit

**Model 1**
```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1_1 <-  unnest(results1, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1_1)
```
**Model 2**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1_2 <-  unnest(results2, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1_2)
```
**Model 3**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1_3 <-  unnest(results3, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1_3)
```
**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=5}
gg_gof1_4 <-  unnest(results4, gof) %>%
    # filter(focus == "mean") %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package))) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() + coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof1_4)
```

### Goodness of fit per condition

**Model 1**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2_1 <- unnest(results1, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2_1)
```
**Model 2**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2_2 <- unnest(results2, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2_2)
```
**Model 3**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2_3 <- unnest(results3, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2_3)
```
**Model Original**

```{r, echo = FALSE, warning=FALSE, fig.width=9.5, fig.height=4.5}
gg_gof2_4 <- unnest(results4, gof_group) %>%
    ggplot(aes(y = p, 
               x = interaction(method, pooling, package), 
               col = condition)) + 
    geom_point(size=2) + ylim(0, 1) + 
    geom_hline(yintercept = .05, lty = 2)+
    theme_bw() +
    coord_flip() +
    facet_wrap(~focus) +
    ggtitle("Goodness of fit")
plot(gg_gof2_4)
```
